---
title: "02B.Standard_length: Hatchlings"
author: "Elliott Schmidt"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true  
    toc_depth: 2
    toc_float: true
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    highlight: monochrome
    theme: cerulean
    latex_engine: xelatex
---

# Load libraries

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse) # data manipulation
library(ggpubr) # producing data exploratory plots
library(modelsummary) # descriptive data 
library(glmmTMB) # running generalised mixed models 
library(DHARMa) # model diagnostics 
library(performance) # model diagnostics  
library(ggeffects) # partial effect plots 
library(car) # running Anova on model 
library(emmeans) # post-hoc analysis  
library(MuMIn) 
library(patchwork)
``` 

# Import data

```{r message=FALSE, warning=FALSE}
hatch <- read_csv("import_data/SL_hatchling.csv") |> 
  mutate(across(1:14,factor)) |> 
  mutate(STANDARD_LENGTH =SL, 
         .keep = "unused") |> 
  mutate(STANDARD_LENGTH =as.numeric(STANDARD_LENGTH)) |>
  drop_na(STANDARD_LENGTH)

m2.5 <- read_csv("import_data/2-5_month_size_data_2022_2023.csv") |> 
  mutate(across(1:15,factor)) |> 
  mutate(STANDARD_LENGTH =LENGTH, 
         .keep = "unused") |> 
  select(!(NOTES)) |> 
  select(1:15,"STANDARD_LENGTH","MASS")|> 
  group_by(CLUTCH_NUMBER) |> 
  mutate(DENSITY = n()) |> 
  ungroup()

adult <- read_csv("import_data/adult_size_2022_2023.csv") |> 
  mutate(across(1:3,factor), 
         MALE = FISH_ID, 
         FEMALE = FISH_ID, 
         POPULATION = str_sub(FISH_ID, 2,4), 
         POPULATION = case_when(POPULATION == "ARL" ~ "Arlington Reef", 
                                POPULATION == "SUD" ~ "Sudbury Reef",
                                POPULATION == "VLA" ~ "Vlassof cay",
                                POPULATION == "PRE" ~ "Pretty patches", 
                                TRUE ~ POPULATION)) |> 
  left_join(select(m2.5, c("MALE","TEMPERATURE")), 
             by="MALE") |> 
  left_join(select(m2.5, c("FEMALE","TEMPERATURE")), 
             by="FEMALE") |>
  distinct() |> 
  mutate(TEMPERATURE = coalesce(TEMPERATURE.x, TEMPERATURE.y)) |> 
  drop_na(TEMPERATURE) |> 
  select(-c("TEMPERATURE.x","TEMPERATURE.y")) 
```

# Data manipulation

```{r}
hatch_df_all <- hatch |> 
  left_join(select(adult, c("MALE", "SL", "MASS")), 
            by ="MALE") |> 
  mutate(SL_MALE =SL, 
         MASS_MALE =MASS, 
         .keep = "unused") |>
  left_join(select(adult, c("FEMALE", "SL", "MASS")), 
            by ="FEMALE") |> 
  mutate(SL_FEMALE =SL, 
         MASS_FEMALE =MASS, 
         .keep ="unused") |> 
  mutate(SL_MIDPOINT = (SL_MALE+SL_FEMALE)/2, 
         MASS_MIDPOINT = (MASS_MALE+MASS_FEMALE)/2) 

hatch_df <- hatch_df_all |> 
  group_by(CLUTCH_NUMBER) |> 
  mutate(MEDIAN_STANDARD_LENGTH = median(STANDARD_LENGTH)) |> 
  drop_na(MEDIAN_STANDARD_LENGTH) |>
  ungroup() |> 
  select(-c("STANDARD_LENGTH","SAMPLE","DATA_EGGS_FOUND")) |> 
  distinct() |> 
  mutate(MASS_MIDPOINT =coalesce(MASS_MIDPOINT, MASS_MALE), 
         SL_MIDPOINT =coalesce(SL_MIDPOINT, SL_MALE))
```

# Models

## Random factors
```{r}
modelNULL <- glmmTMB(STANDARD_LENGTH ~ 1, 
                  family=gaussian(),
                  data =hatch_df_all)

model1 <- glmmTMB(STANDARD_LENGTH ~ (1|MALE), 
                  family=gaussian(),
                  data = hatch_df_all)

model2 <- glmmTMB(STANDARD_LENGTH ~ (1|MALE/CLUTCH_NUMBER) , 
                  family=gaussian(),
                  data = hatch_df_all) 

AIC(modelNULL, model1, model2) 
BIC(modelNULL, model1, model2)
```

## Main hypothesis

```{r}
model1a <- glmmTMB(STANDARD_LENGTH ~ scale(SL_MALE, center=TRUE)*TEMPERATURE + (1| MALE),                     
                   family=gaussian(), 
                   data=hatch_df_all)
```

## Alternative hypothesis

```{r}
model1b <- glmmTMB(STANDARD_LENGTH ~ scale(SL_MALE, center=TRUE)*TEMPERATURE + scale(as.numeric(DAYS_IN_TREATMENT), center=TRUE) +(1| MALE),
                   family=gaussian(), 
                   data=hatch_df_all)
```

## Model selection

```{r}
AICc(model1a, model1b, k=4) 
``` 

# Model validation {.tabset}

## DHARMa

```{r}
model1b |> 
  simulateResiduals(plot=TRUE)  

model1b |> testResiduals(plot=T) 
```

## performance 
```{r}
check_model(model1b, detrend =FALSE)
``` 

## {-} 

# Partial effect plots

```{r warning=FALSE, message=FALSE}
model1b |> ggemmeans(~SL_MALE|TEMPERATURE) |> 
  plot(add.data =TRUE) 

model1b |> ggemmeans(~TEMPERATURE) |> 
  plot(add.data =TRUE)  
 
```

# Model investigation {.tabset}

## Summary

```{r}
model1b |> summary()
```

## Anova

```{r}
model1b |> Anova()
```

## Confint

```{r}
model1b |> confint()
```

## r-squared

```{r}
model1b |> r2_nakagawa()
```

## {-} 

# Post-hoc analysis 

## emmeans 

```{r}
model1b |> emmeans(pairwise ~TEMPERATURE, type ="response")
```


## emtrends 

```{r}
model1b |> emtrends(var = "SL_MALE", type="response") |> summary()
model1b |> emtrends(var = "SL_MALE", type="response") |> pairs() |>  summary() 
```

# Summary figure

```{r fig.height = 8, fig.width=12}
hatch.sl <- emmeans(model1b, ~ SL_MALE*TEMPERATURE, 
                 at =list(SL_MALE=seq(from =min(hatch_df$SL_MALE), to =max(hatch_df$SL_MALE), by=.25)))

hatch.sl.df <- as.data.frame(hatch.sl)

hatch.sl.obs <- drop_na(hatch_df_all, SL_MALE, STANDARD_LENGTH) |> 
  mutate(Pred =predict(model1b, re.form=NA, type ='response'), 
         Resid =residuals(model1b, type ='response'), 
         Fit =Pred+Resid) 

hatch.sl.obs.summarize <-  hatch.sl.obs |> 
  group_by(MALE, TEMPERATURE) |> 
  summarise(mean.sl =mean(Fit, na.rm=TRUE), 
            mean.sl.male =mean(SL_MALE, na.rm = TRUE), 
            sd.sl =sd(Fit, na.rm =TRUE), 
            n.sl = n()) |> 
  mutate(se.sl = sd.sl / sqrt(n.sl), 
         lower.ci.sl =mean.sl - qt(1-(0.05/2), n.sl -1) * se.sl, 
         upper.ci.sl =mean.sl + qt(1-(0.05/2), n.sl -1) * se.sl) |> 
  ungroup()

mod = lm(mean.sl ~ mean.sl.male*TEMPERATURE, 
         data =hatch.sl.obs.summarize)
mod.sl <- emmeans(mod, ~ mean.sl.male*TEMPERATURE, 
                 at =list(mean.sl.male=seq(from =min(hatch.sl.obs.summarize$mean.sl.male), to =max(hatch.sl.obs.summarize$mean.sl.male), by=.25))) |> as.data.frame()

hatch.plot <- ggplot(data = hatch.sl.df, aes(x=SL_MALE, y=emmean))  + 
  stat_smooth(data=hatch.sl.obs.summarize, aes(x =mean.sl.male,
                                            y =mean.sl, color=TEMPERATURE), 
              method = "lm", 
              se=FALSE) + 
  geom_ribbon(data=mod.sl, aes(x =mean.sl.male,
                               y =emmean, 
                               ymin=lower.CL, 
                               ymax=upper.CL, 
                               fill=TEMPERATURE), 
              alpha=0.5) +
  geom_pointrange(data = hatch.sl.obs.summarize, aes(x =mean.sl.male, 
                                                  y =mean.sl, 
                                                  ymin =lower.ci.sl, 
                                                  ymax =upper.ci.sl, 
                                                  color = TEMPERATURE)) +  
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  scale_fill_manual(values =c("#69d7d8","#ff9c56", "#903146")) +
  facet_wrap(~TEMPERATURE)+
  scale_y_continuous(limits = c(0.3,0.7), breaks = seq(0.3,0.7,by=0.1))+
  xlab("PARENTAL MALE STANDARD LENGTH (mm)") + 
  ylab("OFFSPRING STANDARD LENGTH (mm)") + 
  ggtitle("Offspring-male relationship") +
  theme_classic()+theme(legend.position = 'none')

hatch.sl.obs.summarize2 <- hatch.sl.obs.summarize |> 
  group_by(TEMPERATURE) |> 
  mutate(temp_mean =mean(mean.sl), 
         temp_sd =sd(mean.sl)) |> 
  distinct(temp_mean, .keep_all = TRUE)

hatch.plot2 <- ggplot(hatch.sl.obs.summarize, aes(x=TEMPERATURE, y=mean.sl, color=TEMPERATURE)) + 
  geom_pointrange(data=hatch.sl.obs.summarize2, 
                  aes(x=TEMPERATURE, 
                      y=temp_mean, 
                      ymin=temp_mean - temp_sd, 
                      ymax=temp_mean + temp_sd), 
                  size = 1) + 
  geom_jitter(width=0.05, 
              alpha=0.3) +  
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  scale_fill_manual(values =c("#69d7d8","#ff9c56", "#903146")) +
  scale_y_continuous(limits = c(0.3,0.7), breaks = seq(0.3,0.7,by=0.1))+
  theme_classic() + 
  ylab("") + 
  theme(legend.position = c(0.8,0.9), 
                                legend.box.background = element_rect(color = "black", size=2))

hatch.plot.final <-hatch.plot + hatch.plot2 + 
  plot_layout(guides = "collect" & theme(legend.position = "bottom"), 
              widths = c(2,1)); hatch.plot.final
```

```{r eval=FALSE, echo=FALSE}
hatch.density <- ggdensity(hatch.sl.obs, x="Fit", 
          color = "TEMPERATURE", 
          fill = "TEMPERATURE", 
          rug=TRUE, 
          add="median", 
          alpha=0.5,
          palette=c("#69d7d8","#ff9c56", "#903146")) + 
  
  scale_x_continuous(limits = c(0.3,0.7), breaks = seq(0.3,0.7,by=0.1))+
          clean_theme() + rotate() + 
  theme(legend.position = c(0.7,0.9), 
                                legend.box.background = element_rect(color = "black", size=2))
```

# slopes

```{r}
add.df <- split(hatch.sl.obs.summarize, hatch.sl.obs.summarize$TEMPERATURE) |> 
  map(~lm(mean.sl ~ mean.sl.male, data=.)) |> 
  map(summary) |> 
  map_dbl("r.squared") |> 
  as.data.frame()

add.df <- add.df |>
  mutate(TEMPERATURE = row.names(add.df)) |>
  rename(r.sqaured =names(add.df)[1]) 

df.results.1 <- hatch.sl.obs.summarize |> 
  group_by(TEMPERATURE) |> 
  do({ 
    mod = lm(mean.sl ~ mean.sl.male, data = .) 
    data.frame(group = "1-months", 
               Slope = coef(mod)[2], 
               Heritability = coef(mod)[2]*2)
    }) |> 
  as.data.frame() |> 
  mutate(Heritability = case_when(Heritability <=0 ~ 0, 
                                  TRUE ~ Heritability)) |> 
  inner_join(add.df, by="TEMPERATURE"); df.results.1
``` 

# Within parental variation 

```{r}
cv_within <- hatch.sl.obs |> 
  group_by(MALE) |> 
  mutate(mean_value =mean(Fit), 
         sdr_value =sd(Fit), 
         CV =(sdr_value/mean_value) *100) |>
  ungroup() |> 
  select(-c("DATA_EGGS_FOUND","SAMPLE","STANDARD_LENGTH","Pred","Fit","Resid")) |> 
  distinct(MALE, .keep_all=TRUE)  

ggplot(cv_within, aes(x=mean_value, y=sdr_value)) + 
  geom_point() + 
  geom_smooth(method="lm") +  
  ylab("sd of residuals") + 
  xlab("mean") + 
  theme_classic()

within_var <- aov(CV ~ TEMPERATURE, 
                  data=cv_within) 
summary(within_var) 
emmeans(within_var, ~TEMPERATURE) |> pairs() |> summary()  

cv_within_summ <- cv_within |> 
  group_by(TEMPERATURE) |> 
  mutate(mean_CV =mean(CV), 
         mean_mean =mean(mean_value), 
         mean_sd =mean(sdr_value),
         nsample =n()) |>
  mutate(ser_value = sdr_value/sqrt(nsample), 
         lower.ci =mean_CV - qt(1-(0.05/2), nsample -1) * ser_value, 
         upper.ci =mean_CV + qt(1-(0.05/2), nsample -1) * ser_value) |>
  ungroup() |> 
  distinct(TEMPERATURE, .keep_all=TRUE) |> 
  select(c("TEMPERATURE","mean_CV","mean_mean","mean_sd")); cv_within_summ
```

```{r echo=FALSE, eval=FALSE}
ggplot(cv_within, aes(x=TEMPERATURE, y=CV, color=TEMPERATURE)) + 
  geom_pointrange(data=cv_within_summ, 
                  aes(x=TEMPERATURE, 
                      y=mean_CV, 
                      ymin=lower.ci, 
                      ymax=upper.ci)) + 
  geom_jitter(width=0.05, 
              alpha=0.7) +  
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  scale_fill_manual(values =c("#69d7d8","#ff9c56", "#903146")) +
  theme_classic() + 
  ylab("CVr")
```

# Among parental variation
```{r}
cv_among <-  hatch.sl.obs |> 
  group_by(MALE) |> 
  mutate(mean_value =mean(Fit), 
         sdr_value =sd(Fit), 
         CV =(sdr_value/mean_value) *100) |>
  ungroup() |> 
  select(-c("DATA_EGGS_FOUND","SAMPLE","STANDARD_LENGTH","Pred","Fit","Resid")) |> 
  distinct(MALE, .keep_all=TRUE) |> 
  group_by(TEMPERATURE) |> 
  mutate(mean_among =mean(CV), 
         sdr_among =sd(CV), 
         nsamples=n(),
         cv_among =(sdr_among/mean_among)*100) |> 
  ungroup() |> 
  distinct(cv_among, .keep_all = T) |> 
  select(c("TEMPERATURE","cv_among","sdr_among","mean_among","nsamples")) |> 
  arrange(TEMPERATURE)


##final cv values


cv_among2 <- data.frame(x=c("27v30","28v30","27v28"))
cv_among2$cv_among[1] =log(cv_among$cv_among[1]/cv_among$cv_among[3]) 
cv_among2$cv_among[2] =log(cv_among$cv_among[2]/cv_among$cv_among[3]) 
cv_among2$cv_among[3] =log(cv_among$cv_among[1]/cv_among$cv_among[2]) 

cv_among; cv_among2
```



