---
title: "02A. Maternal Effects and Reproduction: Egg count"
author: "Elliott Schmidt"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true  
    toc_depth: 2
    toc_float: true
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    highlight: monochrome
    theme: cerulean
    latex_engine: xelatex
--- 

# Load libraries

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse) # data manipulation
library(ggpubr) # producing data exploratory plots
library(modelsummary) # descriptive data 
library(glmmTMB) # running generalised mixed models 
library(DHARMa) # model diagnostics 
library(performance) # model diagnostics  
library(ggeffects) # partial effect plots 
library(car) # running Anova on model 
library(emmeans) # post-hoc analysis  
library(MuMIn) # model comparisons
library(lme4)  #blups
library(patchwork) #aligning plots
``` 

# Import data

```{r message=FALSE, warning=FALSE}
egg <- read_csv("import_data/egg_size_data_2022_2023.csv") |> 
  mutate(across(1:14,factor))  |> 
  select(!c(NOTES,...18, IMAGE))   

reprod.data <- read_csv("import_data/clutch_data_2022_2023.csv") |> 
  mutate(across(c(1:7,16,23), factor))  
  

m2.5 <- read_csv("import_data/2-5_month_size_data_2022_2023.csv") |> 
  mutate(across(1:15,factor)) |> 
  mutate(STANDARD_LENGTH =LENGTH, 
         .keep = "unused") |> 
  select(!(NOTES)) |> 
  select(1:15,"STANDARD_LENGTH","MASS")|> 
  group_by(CLUTCH_NUMBER) |> 
  mutate(DENSITY = n()) |> 
  ungroup()

adult <- read_csv("import_data/adult_size_2022_2023.csv") |> 
  mutate(across(1:3,factor), 
         MALE = FISH_ID, 
         FEMALE = FISH_ID, 
         POPULATION = str_sub(FISH_ID, 2,4), 
         POPULATION = case_when(POPULATION == "ARL" ~ "Arlington Reef", 
                                POPULATION == "SUD" ~ "Sudbury Reef",
                                POPULATION == "VLA" ~ "Vlassof cay",
                                POPULATION == "PRE" ~ "Pretty patches", 
                                TRUE ~ POPULATION)) |> 
  left_join(select(m2.5, c("MALE","TEMPERATURE")), 
             by="MALE") |> 
  left_join(select(m2.5, c("FEMALE","TEMPERATURE")), 
             by="FEMALE") |>
  distinct() |> 
  mutate(TEMPERATURE = coalesce(TEMPERATURE.x, TEMPERATURE.y)) |> 
  drop_na(TEMPERATURE) |> 
  select(-c("TEMPERATURE.x","TEMPERATURE.y")) 
```

# Data manipulation

```{r}
m2.5_df_all <- m2.5 |> 
  left_join(select(adult, c("MALE", "SL", "MASS")), 
            by ="MALE") |> 
  mutate(SL_MALE =SL, 
         MASS_MALE =MASS.y, 
         .keep = "unused") |>
  left_join(select(adult, c("FEMALE", "SL", "MASS")), 
            by ="FEMALE") |> 
  mutate(SL_FEMALE =SL, 
         MASS_FEMALE =MASS, 
         .keep ="unused") |> 
  mutate(SL_MIDPOINT = (SL_MALE+SL_FEMALE)/2, 
         MASS_MIDPOINT = (MASS_MALE+MASS_FEMALE)/2) 

m2.5_df <- m2.5_df_all |>
  group_by(CLUTCH_NUMBER) |> 
  mutate(MEDIAN_STANDARD_LENGTH = median(STANDARD_LENGTH)) |>
  drop_na(MEDIAN_STANDARD_LENGTH) |>
  ungroup() |> 
  select(-c("STANDARD_LENGTH","MASS.x")) |> 
  distinct() |> 
  mutate(MASS_MIDPOINT =coalesce(MASS_MIDPOINT, MASS_MALE), 
         SL_MIDPOINT =coalesce(SL_MIDPOINT, SL_MALE)) 

clutches <- m2.5_df |> 
  select(CLUTCH_NUMBER)
egg_df_all <- egg |> 
  left_join(select(adult, c("MALE", "SL", "MASS")), 
            by ="MALE")  |> 
  mutate(SL_MALE =SL, 
         MASS_MALE =MASS, 
         .keep = "unused") |>
  left_join(select(adult, c("FEMALE", "SL", "MASS")), 
            by ="FEMALE") |> 
  mutate(SL_FEMALE =SL, 
         MASS_FEMALE =MASS, 
         .keep ="unused") |> 
  mutate(SL_MIDPOINT = (SL_MALE+SL_FEMALE)/2, 
         MASS_MIDPOINT = (MASS_MALE+MASS_FEMALE)/2) |> 
  left_join(select(reprod.data, c("CLUTCH_NUMBER","EGG_COUNT","HATCHING_SUCCESS")), by="CLUTCH_NUMBER")

egg_df <- egg_df_all |>
  group_by(CLUTCH_NUMBER) |> 
  mutate(MEDIAN_EGG_SIZE = median(EGG_SIZE)) |> 
  drop_na(MEDIAN_EGG_SIZE) |>
  ungroup()  |> 
  select(-c("EGG_SIZE","SAMPLE")) |> 
  distinct() |> 
  mutate(MASS_MIDPOINT =coalesce(MASS_MIDPOINT, MASS_MALE), 
         SL_MIDPOINT =coalesce(SL_MIDPOINT, SL_MALE), 
         SL_FEMALE =coalesce(SL_FEMALE, SL_MALE))  # done for two individuals
  
egg_df <- clutches |> 
  inner_join(egg_df, by="CLUTCH_NUMBER") 
```

# Exploratory data analysis 

```{r fig.width=12, fig.height=6, warning=FALSE, message=FALSE}
plot1 <- ggplot(egg_df, aes(x=MASS_FEMALE, y=MEDIAN_EGG_SIZE, color=TEMPERATURE)) +
  geom_point(alpha=0.05) + 
  stat_smooth(method = "lm", se=FALSE) +
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  ggtitle("EGG SIZE") +
  theme_classic()

plot2 <- ggplot(egg_df, aes(x=MASS_FEMALE, y=EGG_COUNT, color=TEMPERATURE)) +
  geom_point(alpha=0.05) + 
  stat_smooth(method = "lm", se=FALSE) +
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  ggtitle("EGG COUNT") +
  theme_classic() 

plot3 <- ggplot(egg_df, aes(x=as.numeric(DAYS_IN_TREATMENT), y=EGG_COUNT, color=TEMPERATURE)) +
  geom_point(alpha=0.05) + 
  stat_smooth(method = "lm", se=FALSE) +
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  ggtitle("EGG COUNT") +
  theme_classic()

ggarrange(plot1, plot2, 
          nrow=1, 
          ncol=2, 
          common.legend = TRUE)
```

# Descriptive statistics 

```{r}
datasummary(Factor(POPULATION) ~ Factor(TEMPERATURE), 
            data=egg_df, 
            fmt = "%.0f") 
```

```{r}
datasummary(Factor(TEMPERATURE) ~ EGG_SIZE * (NUnique + mean + median + min + max + sd + Histogram), 
            data = drop_na(egg_df_all),  
            fmt = "%.2f")
```  

# Fit models [random factors] 

```{r}
modelNULL <- glmmTMB(EGG_COUNT ~ 1, 
                  family=gaussian(),
                  data =egg_df)

model1 <- glmmTMB(EGG_COUNT ~ (1|CLUTCH_ORDER), 
                  family=gaussian(),
                  data = egg_df)

model2 <- glmmTMB(EGG_COUNT ~ (1|POPULATION), 
                  family=gaussian(),
                  data = egg_df)  

model3 <- glmmTMB(EGG_COUNT ~ (1|FEMALE), 
                  family=gaussian(),
                  data = egg_df)

model4 <- glmmTMB(EGG_COUNT ~ (1|FEMALE) + (1|POPULATION), 
                  family=gaussian(),
                  data = egg_df)

AIC(modelNULL, model1, model2, model3, model4, k=3) 
BIC(modelNULL, model1, model2, model3, model4)
```

# Fit fixed factors

## Main hypothesis

```{r}
model1a <- glmmTMB(EGG_COUNT ~ scale(MASS_FEMALE, center=TRUE)*TEMPERATURE + scale(MEDIAN_EGG_SIZE, center=TRUE) + (1|FEMALE), 
                    family=gaussian(), 
                    data=egg_df)
```

## Alternative hypothesis

```{r}
model1b <- glmmTMB(EGG_COUNT ~ scale(MASS_FEMALE, center=TRUE)*TEMPERATURE + scale(as.numeric(DAYS_IN_TREATMENT), center=TRUE) + scale(MEDIAN_EGG_SIZE, center=TRUE) +  (1|FEMALE), 
                    family=gaussian(), 
                    data=egg_df)
```

## Model selection

```{r}
AICc(model1a, model1b, k=5) 
```

# Model validation {.tabset}

## DHARMa

```{r}
model1a |> 
  simulateResiduals(plot=TRUE)  

model1a |> testResiduals(plot=T) 
``` 

## performance 

```{r}
check_model(model1a, detrend=FALSE)
``` 

## {-} 

# Partial effect plots

```{r}
model1a |> ggemmeans(~MASS_FEMALE) |> 
  plot(add.data =TRUE) 

model1a |> ggemmeans(~TEMPERATURE) |> 
  plot(add.data =FALSE)

model1a |> ggemmeans(~MEDIAN_EGG_SIZE) |> 
  plot(add.data =TRUE) 

model1a |> ggemmeans(~MASS_FEMALE|TEMPERATURE) |> 
  plot(add.data =TRUE)
``` 

# Model investigation {.tabset}

## Summary

```{r}
model1a |> summary()
```

## Anova

```{r}
model1a |> Anova()
```

## Confint

```{r}
model1a |> confint()
```

## r-squared

```{r}
model1a |> r2_nakagawa()
```

## {-} 

# Summary figure 

```{r warning=FALSE}
egg_df <- egg_df |> drop_na(EGG_COUNT, MASS_FEMALE, MEDIAN_EGG_SIZE)
egg.emm <- emmeans(model1a, ~ MASS_FEMALE*TEMPERATURE, 
                 at =list(MASS_FEMALE=seq(from =min(egg_df$MASS_FEMALE), to =max(egg_df$MASS_FEMALE), by=.25)))

eggcount.df <- as.data.frame(egg.emm)

eggcount.obs <- egg_df |> 
  mutate(Pred =predict(model1a, re.form=NA, type ='response'), 
         Resid =residuals(model1a, type ='response'), 
         Fit =Pred+Resid) 

eggcount.obs.summarize <-  eggcount.obs |> 
  group_by(FEMALE, TEMPERATURE) |> 
  summarise(mean.eggcount =mean(Fit, na.rm=TRUE), 
            mean.mass.female =mean(MASS_FEMALE, na.rm = TRUE), 
            min.eggcount =min(Fit, na.rm=TRUE), 
            max.eggcount =max(Fit, na.rm=TRUE),
            sd.eggcount =sd(Fit, na.rm =TRUE), 
            n.eggcount = n()) |> 
  mutate(se.eggcount = sd.eggcount / sqrt(n.eggcount), 
         lower.ci.eggcount =mean.eggcount - qt(1-(0.05/2), n.eggcount -1) * se.eggcount, 
         upper.ci.eggcount =mean.eggcount + qt(1-(0.05/2), n.eggcount -1) * se.eggcount) |> 
  ungroup()

eggcount.plot <- ggplot(data = eggcount.df, aes(x=MASS_FEMALE, y=emmean)) + 
  stat_smooth(aes(color=TEMPERATURE), 
              method = "lm") + 
  geom_ribbon(aes(ymin=lower.CL, ymax=upper.CL, fill=TEMPERATURE), alpha=0.5) +
  geom_pointrange(data = eggcount.obs.summarize, aes(x =mean.mass.female, 
                                                  y =mean.eggcount, 
                                                  ymin =min.eggcount, 
                                                  ymax =max.eggcount, 
                                                  color = TEMPERATURE)) +  
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  scale_fill_manual(values =c("#69d7d8","#ff9c56", "#903146")) +
  scale_y_continuous(limits = c(0,1000), breaks=seq(0, 1000, 100)) +
  facet_wrap(~TEMPERATURE)+
  xlab("MATERNAL MASS (g)") + 
  ylab("Clutch size") + 
  ggtitle("Maternal-clutch size relationship") +
  theme_classic() + 
  theme(legend.position = "none")

eggcount.density <- ggdensity(eggcount.obs, x="Fit", 
          color = "TEMPERATURE", 
          fill = "TEMPERATURE", 
          rug=TRUE, 
          add="median", 
          alpha=0.5,
          palette=c("#69d7d8","#ff9c56", "#903146")) + 
          clean_theme() + rotate() + 
  theme(legend.position = c(0.7,0.9), 
                                legend.box.background = element_rect(color = "black", size=1.5))

eggcount.plot.final <-eggcount.plot + eggcount.density + 
  plot_layout(guides = "collect" & theme(legend.position = "bottom"), 
              widths = c(2,1)); eggcount.plot.final
```

# slopes

```{r}
add.df <- split(eggcount.obs.summarize, eggcount.obs.summarize$TEMPERATURE) |> 
  map(~lm(mean.eggcount ~ mean.mass.female, data=.)) |> 
  map(summary) |> 
  map_dbl("r.squared") |> 
  as.data.frame()

add.df <- add.df |>
  mutate(TEMPERATURE = row.names(add.df)) |>
  rename(r.sqaured =names(add.df)[1]) 

df.results.eggcount <- eggcount.obs.summarize |> 
  group_by(TEMPERATURE) |> 
  do({ 
    mod = lm(scale(mean.eggcount) ~ mean.mass.female, data = .) 
    data.frame(group = "egg_count", 
               Slope = coef(mod)[2], 
               Heritability = coef(mod)[2]*2)
    }) |> 
  as.data.frame() |> 
  mutate(Heritability = case_when(Heritability <=0 ~ 0, 
                                  TRUE ~ Heritability)) |> 
  inner_join(add.df, by="TEMPERATURE"); df.results.eggcount
``` 

# variation among clutches
```{r}
cv_among <- eggcount.obs |> 
  distinct(FEMALE, .keep_all=TRUE) |> 
  group_by(TEMPERATURE) |> 
  mutate(mean_among =mean(Fit), 
         sd_among =sd(Fit), 
         cv_among =(sd_among/mean_among)*100) |> 
  ungroup() |> 
  distinct(cv_among, .keep_all = T) |> 
  select(c("TEMPERATURE","cv_among")) |> 
  arrange(as.numeric(TEMPERATURE))
cv_among
```