---
title: "02C.GrowthRate"
author: "Elliott Schmidt"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true  
    toc_depth: 2
    toc_float: true
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    highlight: monochrome
    theme: cerulean
    latex_engine: xelatex
---

# Load libraries

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse) # data manipulation
library(ggpubr) # producing data exploratory plots
library(modelsummary) # descriptive data 
library(glmmTMB) # running generalised mixed models 
library(DHARMa) # model diagnostics 
library(performance) # model diagnostics  
library(ggeffects) # partial effect plots 
library(car) # running Anova on model 
library(emmeans) # post-hoc analysis  
library(MuMIn) 
library(patchwork) 
library(ggridges)
``` 

# Import data

```{r message=FALSE, warning=FALSE}
hatch <- read_csv("import_data/SL_hatchling.csv") |> 
  mutate(across(1:14,factor)) |> 
  mutate(STANDARD_LENGTH =SL, 
         .keep = "unused") |> 
  mutate(STANDARD_LENGTH =as.numeric(STANDARD_LENGTH)) |>
  drop_na(STANDARD_LENGTH)

m1 <- read_csv("import_data/1_month_size_data_2022_2023.csv") |> 
  mutate(across(1:15,factor)) |> 
  mutate(STANDARD_LENGTH =LENGTH, 
         .keep = "unused") |> 
  select(!(NOTES)) |> 
  select(1:15,"STANDARD_LENGTH","MASS") |> 
  group_by(CLUTCH_NUMBER) |> 
  mutate(DENSITY = n()) |> 
  ungroup()
           
m2 <- read_csv("import_data/2_month_size_data_2022_2023.csv") |> 
  mutate(across(1:15,factor)) |> 
  mutate(STANDARD_LENGTH =LENGTH, 
         .keep = "unused") |> 
  select(!(NOTES)) |> 
  select(1:15,"STANDARD_LENGTH","MASS")|> 
  group_by(CLUTCH_NUMBER) |> 
  mutate(DENSITY = n()) |> 
  ungroup()

m3 <- read_csv("import_data/2-5_month_size_data_2022_2023.csv") |> 
  mutate(across(1:15,factor)) |> 
  mutate(STANDARD_LENGTH =LENGTH, 
         .keep = "unused") |> 
  select(!(NOTES)) |> 
  select(1:15,"STANDARD_LENGTH","MASS")|> 
  group_by(CLUTCH_NUMBER) |> 
  mutate(DENSITY = n()) |> 
  ungroup()

adult <- read_csv("import_data/adult_size_2022_2023.csv") |> 
  mutate(across(1:3,factor), 
         MALE = FISH_ID, 
         FEMALE = FISH_ID, 
         POPULATION = str_sub(FISH_ID, 2,4), 
         POPULATION = case_when(POPULATION == "ARL" ~ "Arlington Reef", 
                                POPULATION == "SUD" ~ "Sudbury Reef",
                                POPULATION == "VLA" ~ "Vlassof cay",
                                POPULATION == "PRE" ~ "Pretty patches", 
                                TRUE ~ POPULATION)) |> 
  left_join(select(m3, c("MALE","TEMPERATURE")), 
             by="MALE") |> 
  left_join(select(m3, c("FEMALE","TEMPERATURE")), 
             by="FEMALE") |>
  distinct() |> 
  mutate(TEMPERATURE = coalesce(TEMPERATURE.x, TEMPERATURE.y)) |> 
  drop_na(TEMPERATURE) |> 
  select(-c("TEMPERATURE.x","TEMPERATURE.y")) 
```

# Data manipulation

```{r}
hatch_df_all <- hatch |> 
  left_join(select(adult, c("MALE", "SL", "MASS")), 
            by ="MALE") |> 
  mutate(SL_MALE =SL, 
         MASS_MALE =MASS, 
         .keep = "unused") |>
  left_join(select(adult, c("FEMALE", "SL", "MASS")), 
            by ="FEMALE") |> 
  mutate(SL_FEMALE =SL, 
         MASS_FEMALE =MASS, 
         .keep ="unused") |> 
  mutate(SL_MIDPOINT = (SL_MALE+SL_FEMALE)/2, 
         MASS_MIDPOINT = (MASS_MALE+MASS_FEMALE)/2, 
         PARENTAL_DAYS_IN_TREATMENT =DAYS_IN_TREATMENT, 
         DENSITY =1, 
         AGE_DAYS=0) |> 
  select(c("CLUTCH_NUMBER","MALE","FEMALE","REGION","POPULATION","TEMPERATURE",
           "TANK","CLUTCH_ORDER","PARENTAL_DAYS_IN_TREATMENT","DENSITY","AGE_DAYS","STANDARD_LENGTH", 
           "SL_MALE","MASS_MALE")) |> 
  mutate(AGE ="hatch")

m1_df_all <- m1 |> 
  left_join(select(adult, c("MALE", "SL", "MASS")), 
            by ="MALE") |> 
  mutate(SL_MALE =SL, 
         MASS_MALE =MASS.y, 
         .keep = "unused") |>
  left_join(select(adult, c("FEMALE", "SL", "MASS")), 
            by ="FEMALE") |> 
  mutate(SL_FEMALE =SL, 
         MASS_FEMALE =MASS, 
         .keep ="unused") |> 
  mutate(SL_MIDPOINT = (SL_MALE+SL_FEMALE)/2, 
         MASS_MIDPOINT = (MASS_MALE+MASS_FEMALE)/2, 
         AGE_DAYS=30)  |> 
  select(c("CLUTCH_NUMBER","MALE","FEMALE","REGION","POPULATION","TEMPERATURE",
           "TANK","CLUTCH_ORDER","PARENTAL_DAYS_IN_TREATMENT","DENSITY","AGE_DAYS","STANDARD_LENGTH", 
           "SL_MALE","MASS_MALE")) |> 
  mutate(AGE ="1months")

m2_df_all <- m2 |> 
  left_join(select(adult, c("MALE", "SL", "MASS")), 
            by ="MALE") |> 
  mutate(SL_MALE =SL, 
         MASS_MALE =MASS.y, 
         .keep = "unused") |>
  left_join(select(adult, c("FEMALE", "SL", "MASS")), 
            by ="FEMALE") |> 
  mutate(SL_FEMALE =SL, 
         MASS_FEMALE =MASS, 
         .keep ="unused") |> 
  mutate(SL_MIDPOINT = (SL_MALE+SL_FEMALE)/2, 
         MASS_MIDPOINT = (MASS_MALE+MASS_FEMALE)/2, 
         AGE_DAYS=60)  |> 
  select(c("CLUTCH_NUMBER","MALE","FEMALE","REGION","POPULATION","TEMPERATURE",
           "TANK","CLUTCH_ORDER","PARENTAL_DAYS_IN_TREATMENT","DENSITY","AGE_DAYS","STANDARD_LENGTH", 
           "SL_MALE","MASS_MALE")) |> 
  mutate(AGE ="2months")

m3_df_all <- m3 |> 
  left_join(select(adult, c("MALE", "SL", "MASS")), 
            by ="MALE") |> 
  mutate(SL_MALE =SL, 
         MASS_MALE =MASS.y, 
         .keep = "unused") |>
  left_join(select(adult, c("FEMALE", "SL", "MASS")), 
            by ="FEMALE") |> 
  mutate(SL_FEMALE =SL, 
         MASS_FEMALE =MASS, 
         .keep ="unused") |> 
  mutate(SL_MIDPOINT = (SL_MALE+SL_FEMALE)/2, 
         MASS_MIDPOINT = (MASS_MALE+MASS_FEMALE)/2)  |> 
  select(c("CLUTCH_NUMBER","MALE","FEMALE","REGION","POPULATION","TEMPERATURE",
           "TANK","CLUTCH_ORDER","PARENTAL_DAYS_IN_TREATMENT","DENSITY","AGE_DAYS", "STANDARD_LENGTH", 
           "SL_MALE","MASS_MALE")) |> 
  mutate(AGE ="2.5months")

growth_data <- rbind(hatch_df_all, m1_df_all, m2_df_all, m3_df_all) |> 
  mutate(AGE =factor(AGE), 
         AGE_DAYS =as.numeric(AGE_DAYS)) |> 
  mutate(AGE =fct_relevel(AGE, c("hatch","1months","2months","2.5months")))
```

# exploratory data analysis 

```{r}
ggplot(growth_data, aes(x=as.numeric(factor(AGE)), y=STANDARD_LENGTH)) + 
         geom_point() + 
         stat_smooth(method="lm", 
                     formula=y~poly(x,2, raw=TRUE))

ggplot(growth_data, aes(x=as.numeric(factor(AGE)), y=STANDARD_LENGTH, color=TEMPERATURE)) + 
         geom_point() + 
         stat_smooth(method="lm", 
                     formula=y~poly(x,2, raw=TRUE))
```



# Models

## Random factors
```{r}
modelNULL <- glmmTMB(STANDARD_LENGTH ~ 1, 
                  family=gaussian(),
                  data =growth_data)

model1 <- glmmTMB(STANDARD_LENGTH ~ (1|MALE), 
                  family=gaussian(),
                  data = growth_data)

AIC(modelNULL, model1) 
BIC(modelNULL, model1)
```

## Main hypothesis

```{r}
model1a <- glmmTMB(STANDARD_LENGTH ~ scale(as.numeric(AGE_DAYS))*TEMPERATURE + scale(DENSITY, center=TRUE) + scale(SL_MALE, center=TRUE) + (1| MALE),                 
                   family=gaussian(), 
                   dispformula = ~AGE,
                   data=growth_data)

model1a.p2 <- glmmTMB(STANDARD_LENGTH ~ scale(poly(as.numeric(AGE_DAYS),2, raw=TRUE))*TEMPERATURE + scale(DENSITY, center=TRUE) + scale(SL_MALE, center=TRUE) + (1| MALE),                 
                   family=gaussian(), 
                   dispformula = ~AGE,
                   data=growth_data)

```

## Alternative hypothesis

```{r}
model1b.p2 <- glmmTMB(STANDARD_LENGTH ~ poly(as.numeric(AGE_DAYS),2, raw=TRUE)*TEMPERATURE + scale(DENSITY, center=TRUE) + scale(SL_MALE, center=TRUE) + scale(as.numeric(PARENTAL_DAYS_IN_TREATMENT), center=TRUE) + (1| MALE),                 
                   family=gaussian(), 
                   dispformula = ~AGE,
                   data=growth_data)
```

## Model selection

```{r}
AIC(model1a, model1a.p2, k=5)
AIC(model1a.p2, model1b.p2,  k=6) 
``` 

# Model validation {.tabset}

## DHARMa

```{r}
model1b.p2 |> 
  simulateResiduals(plot=TRUE)  

model1b.p2 |> testResiduals(plot=T)  
```

## performance 
```{r}
check_model(model1b.p2, detrend =FALSE)
``` 

## {-} 

# Partial effect plots

```{r warning=FALSE, message=FALSE}
model1b.p2 |> ggemmeans(~AGE_DAYS|TEMPERATURE) |> 
  plot(add.data =TRUE) 

model1b.p2 |> ggemmeans(~TEMPERATURE) |> 
  plot(add.data =TRUE)

model1b.p2 |> ggemmeans(~DENSITY) |> 
  plot(add.data =TRUE)

model1b.p2 |> ggemmeans(~SL_MALE) |> 
  plot(add.data =TRUE)

model1b.p2 |> ggemmeans(~PARENTAL_DAYS_IN_TREATMENT) |> 
  plot(add.data =TRUE)
```

# Model investigation {.tabset}

## Summary

```{r}
model1b.p2 |> summary()
```

## Anova

```{r}
model1b.p2 |> Anova()
```

## Confint

```{r}
model1b.p2 |> confint()
```

## r-squared

NULL. Can't find r-squared command that can calculate r-squared for model with dispersion factor. 

## {-} 

# Post-hoc analysis 

```{r}
model1b.p2 |> emtrends(var ="AGE_DAYS", type="response") |> pairs()|> summary(adjust="tukey")
```


# Summary figure 

```{r}
growth <- emmeans(model1b.p2, ~ AGE_DAYS*TEMPERATURE, 
                 at =list(AGE_DAYS=seq(from =min(growth_data$AGE_DAYS), to =max(growth_data$AGE_DAYS), by=.5)))

growth.df <- as.data.frame(growth)

growth.obs <- drop_na(growth_data, AGE_DAYS, STANDARD_LENGTH) |> 
  mutate(Pred =predict(model1b.p2, re.form=NA, type ='response'), 
         Resid =residuals(model1b.p2, type ='response'), 
         Fit =Pred+Resid) 

growth.obs.summarize <-  growth.obs |> 
  group_by(TEMPERATURE, AGE) |> 
  summarise(mean.growth =mean(Fit, na.rm=TRUE), 
            mean.growth.age =mean(AGE_DAYS, na.rm = TRUE), 
            sd.growth =sd(Fit, na.rm =TRUE), 
            n.growth = n()) |> 
  mutate(se.growth = sd.growth / sqrt(n.growth), 
         lower.ci.growth =mean.growth - qt(1-(0.05/2), n.growth -1) * se.growth, 
         upper.ci.growth =mean.growth + qt(1-(0.05/2), n.growth -1) * se.growth) |> 
  ungroup() |> 
  mutate(mean.growth.age =case_when(AGE =="2.5months" ~ 77.40, 
                                    TRUE ~ mean.growth.age)) 



growth.plot <- ggplot(data = growth.df, aes(x=AGE_DAYS, y=emmean)) + 
  stat_smooth(aes(color=TEMPERATURE), 
              method = "lm", 
              formula =y~poly(x ,2, raw=TRUE)) + 
  geom_ribbon(aes(ymin=lower.CL, ymax=upper.CL, fill=TEMPERATURE), alpha=0.3) + 
  geom_pointrange(data = growth.obs.summarize, aes(x =mean.growth.age, 
                                                  y =mean.growth, 
                                                  ymin =lower.ci.growth, 
                                                  ymax =upper.ci.growth, 
                                                  color = TEMPERATURE), 
                  size=1) +  
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  scale_fill_manual(values =c("#69d7d8","#ff9c56", "#903146")) +
  scale_y_continuous(limits = c(0,30), breaks = seq(0,30,by=5))+
  xlab("AGE (DAYS)") + 
  ylab("OFFSPRING STANDARD LENGTH (mm)") + 
  ggtitle("Offspring-male relationship") +
  theme_classic()+theme(legend.position = 'none')
```

```{r}
growth.obs2 <- growth.obs |> filter(AGE != "hatch") 
growth.plot2 <- ggplot(growth.obs2, aes(y=AGE, x=Fit, fill=TEMPERATURE, color=TEMPERATURE)) + 
  geom_density_ridges2(alpha =0.5, 
                       rel_min_height = 0.0001, 
                       scale =2, 
                       quantile_lines =TRUE, 
                       quantile_fun =median) + 
  #facet_wrap(~AGE) +
  scale_x_continuous(limits = c(0.37,35), breaks = seq(0,35,by=5)) +  
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  scale_fill_manual(values =c("#69d7d8","#ff9c56", "#903146")) +
  ylab("")+xlab("STANDARD LEGNTH (mm)")+
  theme_classic()+ 
  theme(legend.position = 'none')
```

```{r}
hatching.obs <- growth.obs |> filter(AGE == "hatch") 
hatch.plot <- ggplot(hatching.obs, aes(y=AGE, x=Fit, fill=TEMPERATURE, color=TEMPERATURE)) + 
  geom_density_ridges2(alpha =0.5, 
                       rel_min_height = 0.0001, 
                       scale =3, 
                       quantile_lines =TRUE, 
                       quantile_fun =median) + 
  #facet_wrap(~AGE) +
  #scale_x_continuous(limits = c(0.37,35), breaks = seq(0,35,by=5)) +  
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  scale_fill_manual(values =c("#69d7d8","#ff9c56", "#903146")) +
  theme_classic()+ xlab("STANDARD LEGNTH (mm)")+
  theme(legend.position = 'none') 

```

```{r fig.width =12, fig.height=8}
layout <- "
AAAAA
BBCCC
"
growth.plot + hatch.plot + growth.plot2 + plot_layout(design = layout)
```

# Coefficient of variance [within-pair-variance]

```{r}
cv_within <- growth.obs |> 
  group_by(MALE, AGE) |> 
  mutate(mean_value =mean(Fit), 
         sd_value =sd(Fit), 
         CV =(sd_value/mean_value) * 100) |>
  ungroup() |> 
  select(-c("STANDARD_LENGTH","Pred","Fit","Resid")) |> 
  distinct(MALE,AGE, .keep_all=TRUE)  

cv_among <- cv_within |> 
  group_by(TEMPERATURE, AGE) |> 
  mutate(mean_among =mean(CV), 
         sd_among =sd(CV), 
         cv_among =(sd_among/mean_among)*100) |> 
  ungroup() |> 
  distinct(cv_among, .keep_all = T) |> 
  arrange(TEMPERATURE) |> 
  select(c("TEMPERATURE","AGE","CV"))
cv_among
```

## model comparisons
```{r}
within_var <- lm(CV ~ AGE_DAYS*TEMPERATURE, 
                 data=cv_within) 

within_var.p2 <- lm(CV ~ poly(AGE_DAYS, 2, raw=TRUE)*TEMPERATURE, 
data =cv_within)

AICc(within_var, within_var.p2, k=3)
```

# model validation {.tabset} 

## DHARMa

```{r}
within_var.p2 |> 
  simulateResiduals(plot=TRUE)  

within_var.p2 |> testResiduals(plot=T)  
```

## performance 
```{r}
check_model(within_var.p2, detrend =FALSE)
``` 

## {-}

# model investigation
```{r}
summary(within_var.p2)
Anova(within_var.p2)
```

# partial plots

```{r warning=FALSE, message=FALSE}
within_var.p2 |> ggemmeans(~AGE_DAYS|TEMPERATURE) |> 
  plot(add.data =TRUE) 

within_var.p2 |> ggemmeans(~TEMPERATURE) |> 
  plot(add.data =TRUE)

within_var.p2 |> ggemmeans(~AGE_DAYS) |> 
  plot(add.data =TRUE)

```

# summary figure 

```{r fig.width=8, fig.height=6}
cv_within.summarize <-  cv_within |> 
  group_by(TEMPERATURE, AGE) |> 
  summarise(mean.cv =mean(CV, na.rm=TRUE), 
            mean.cv.age =mean(AGE_DAYS, na.rm = TRUE), 
            sd.cv =sd(CV, na.rm =TRUE), 
            n.cv = n()) |> 
  mutate(se.cv = sd.cv / sqrt(n.cv), 
         lower.ci.cv =mean.cv - qt(1-(0.05/2), n.cv -1) * se.cv, 
         upper.ci.cv =mean.cv + qt(1-(0.05/2), n.cv -1) * se.cv) |> 
  ungroup() |> 
  mutate(mean.cv.age =case_when(AGE =="2.5months" ~ 77.40, 
                                    TRUE ~ mean.cv.age)) 

cv_within <- cv_within |> 
  mutate(AGE_DAYS =case_when(AGE =="2.5months" ~ 77.40, 
                                    TRUE ~ AGE_DAYS))


cv.plot <- ggplot(cv_within.summarize, aes(x=AGE, y=mean.cv, color = TEMPERATURE)) + 
  geom_jitter(data =cv_within, aes(x=AGE, y=CV), 
              width=0.1, 
              alpha=0.3, 
              size =2)+
  geom_pointrange(aes(x =AGE, 
                      y =mean.cv, 
                      ymin =lower.ci.cv, 
                      ymax =upper.ci.cv, 
                      color = TEMPERATURE), 
                  size=1.25) +  
  geom_point(data=cv_among, aes(x=AGE, y=CV, color="Among CV"),
             shape =15, 
             size =4, 
             show.legend = TRUE) +
  scale_color_manual(values = c("27"="#69d7d8","28.5"="#ff9c56", "30"="#903146","Among CV"="black")) + 
  scale_fill_manual(values =c("27"="#69d7d8","28.5"="#ff9c56", "30"="#903146","Among CV"="black")) +
  ylab("COEFFICIENT OF VARIATION") +
  facet_wrap(~TEMPERATURE) +
  theme_bw() + 
  theme(axis.text.x =element_text(angle=90, vjust=-0 ), 
        legend.position = "right"); cv.plot
```

**Black boxes are CV among breeding pairs, so only one value per AGE|TEMPERATURE.** 