---
title: "02.Data_analysis - Mass"
author: "Elliott Schmidt"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true  
    toc_depth: 2
    toc_float: true
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    highlight: monochrome
    theme: cerulean
    latex_engine: xelatex
---

# Load libraries

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse) # data manipulation
library(ggpubr) # producing data exploratory plots
library(modelsummary) # descriptive data 
library(glmmTMB) # running generalised mixed models 
library(DHARMa) # model diagnostics 
library(performance) # model diagnostics  
library(ggeffects) # partial effect plots 
library(car) # running Anova on model 
library(emmeans) # post-hoc analysis 
```

# Import data

```{r message=FALSE, warning=FALSE}
m1 <- read_csv("import_data/1_month_size_data_2022_2023.csv") |> 
  mutate(across(1:15,factor)) |> 
  mutate(STANDARD_LENGTH =LENGTH, 
         .keep = "unused") |> 
  select(!(NOTES)) |> 
  select(1:15,"STANDARD_LENGTH","MASS") |> 
  group_by(CLUTCH_NUMBER) |> 
  mutate(DENSITY = n()) |> 
  ungroup()
           
m2 <- read_csv("import_data/2_month_size_data_2022_2023.csv") |> 
  mutate(across(1:15,factor)) |> 
  mutate(STANDARD_LENGTH=LENGTH, 
         .keep = "unused") |> 
  select(!(NOTES)) |> 
  select(1:15,"STANDARD_LENGTH","MASS")|> 
  group_by(CLUTCH_NUMBER) |> 
  mutate(DENSITY = n()) |> 
  ungroup()

m2.5 <- read_csv("import_data/2-5_month_size_data_2022_2023.csv") |> 
  mutate(across(1:15,factor)) |> 
  mutate(STANDARD_LENGTH =LENGTH, 
         .keep = "unused") |> 
  select(!(NOTES)) |> 
  select(1:15,"STANDARD_LENGTH","MASS")|> 
  group_by(CLUTCH_NUMBER) |> 
  mutate(DENSITY = n()) |> 
  ungroup()

adult <- read_csv("import_data/adult_size_2022_2023.csv") |> 
  mutate(across(1:3,factor), 
         MALE = FISH_ID, 
         FEMALE = FISH_ID, 
         POPULATION = str_sub(FISH_ID, 2,4), 
         POPULATION = case_when(POPULATION == "ARL" ~ "Arlington Reef", 
                                POPULATION == "SUD" ~ "Sudbury Reef",
                                POPULATION == "VLA" ~ "Vlassof cay",
                                POPULATION == "PRE" ~ "Pretty patches", 
                                TRUE ~ POPULATION)) |> 
  left_join(select(m1, c("MALE","TEMPERATURE")), 
             by="MALE") |> 
  left_join(select(m1, c("FEMALE","TEMPERATURE")), 
             by="FEMALE") |>
  distinct() |> 
  mutate(TEMPERATURE = coalesce(TEMPERATURE.x, TEMPERATURE.y)) |> 
  drop_na(TEMPERATURE) |> 
  select(-c("TEMPERATURE.x","TEMPERATURE.y"))
```

# Data manipulation

```{r}
m1_df <- m1 |> 
  left_join(select(adult, c("MALE", "SL", "MASS")), 
            by ="MALE") |> 
  mutate(SL_MALE =SL, 
         MASS_MALE =MASS.y, 
         .keep = "unused") |>
  left_join(select(adult, c("FEMALE", "SL", "MASS")), 
            by ="FEMALE") |> 
  mutate(SL_FEMALE =SL, 
         MASS_FEMALE =MASS, 
         .keep ="unused") |> 
  mutate(SL_MIDPOINT = (SL_MALE+SL_FEMALE)/2, 
         MASS_MIDPOINT = (MASS_MALE+MASS_FEMALE)/2) |> 
  group_by(CLUTCH_NUMBER) |> 
  mutate(MEDIAN_MASS = median(MASS.x)) |> 
  drop_na(MEDIAN_MASS) |>
  ungroup() |> 
  select(-c("STANDARD_LENGTH","MASS.x", "SAMPLE_NO")) |> 
  distinct() |> 
  mutate(MASS_MIDPOINT =coalesce(MASS_MIDPOINT, MASS_MALE), 
         SL_MIDPOINT =coalesce(SL_MIDPOINT, SL_MALE))

m2_df <- m2 |> 
  left_join(select(adult, c("MALE", "SL", "MASS")), 
            by ="MALE") |> 
  mutate(SL_MALE =SL, 
         MASS_MALE =MASS.y, 
         .keep = "unused") |>
  left_join(select(adult, c("FEMALE", "SL", "MASS")), 
            by ="FEMALE") |> 
  mutate(SL_FEMALE =SL, 
         MASS_FEMALE =MASS, 
         .keep ="unused") |> 
  mutate(SL_MIDPOINT = (SL_MALE+SL_FEMALE)/2, 
         MASS_MIDPOINT = (MASS_MALE+MASS_FEMALE)/2) |> 
  group_by(CLUTCH_NUMBER) |> 
  mutate(MEDIAN_MASS = median(MASS.x)) |> 
  drop_na(MEDIAN_MASS) |>
  ungroup() |> 
  select(-c("STANDARD_LENGTH","MASS.x", "SAMPLE_NO")) |> 
  distinct() |> 
  mutate(MASS_MIDPOINT =coalesce(MASS_MIDPOINT, MASS_MALE), 
         SL_MIDPOINT =coalesce(SL_MIDPOINT, SL_MALE))

m2.5_df <- m2.5 |> 
  left_join(select(adult, c("MALE", "SL", "MASS")), 
            by ="MALE") |> 
  mutate(SL_MALE =SL, 
         MASS_MALE =MASS.y, 
         .keep = "unused") |>
  left_join(select(adult, c("FEMALE", "SL", "MASS")), 
            by ="FEMALE") |> 
  mutate(SL_FEMALE =SL, 
         MASS_FEMALE =MASS, 
         .keep ="unused") |> 
  mutate(SL_MIDPOINT = (SL_MALE+SL_FEMALE)/2, 
         MASS_MIDPOINT = (MASS_MALE+MASS_FEMALE)/2) |> 
  group_by(CLUTCH_NUMBER) |> 
  mutate(MEDIAN_MASS = median(MASS.x)) |> 
  drop_na(MEDIAN_MASS) |>
  ungroup() |> 
  select(-c("STANDARD_LENGTH","MASS.x")) |> 
  distinct() |> 
  mutate(MASS_MIDPOINT =coalesce(MASS_MIDPOINT, MASS_MALE), 
         SL_MIDPOINT =coalesce(SL_MIDPOINT, SL_MALE))|> 
  drop_na(MASS_MALE)

```

# Exploratory data analysis {.tabset}

## MASS

```{r fig.width=12, fig.height=6, warning=FALSE, message=FALSE}
plot1 <- ggplot(m1_df, aes(x=MASS_MALE, y=MEDIAN_MASS, color=TEMPERATURE)) +
  geom_point(alpha=0.05) + 
  stat_smooth(method = "lm") +
  ylim(0,0.15) +
  theme_classic()

plot2 <- ggplot(m1_df, aes(x=MASS_FEMALE, y=MEDIAN_MASS, color=TEMPERATURE)) +
  geom_point(alpha=0.05) + 
  stat_smooth(method = "lm") + 
  ylim(0,0.15) +
  theme_classic()

plot3 <- ggplot(m1_df, aes(x=MASS_MIDPOINT, y=MEDIAN_MASS, color=TEMPERATURE)) +
  geom_point(alpha=0.05) + 
  stat_smooth(method = "lm") + 
  ylim(0,0.15) +
  theme_classic()

ggarrange(plot1, plot2, plot3, 
          nrow =1, 
          ncol =3, 
          common.legend = TRUE)
```

##  {.unnumbered}

# Descriptive statistics {.tabset}

## counts {.tabset}

### Adults

```{r}
datasummary(Factor(POPULATION) ~ Factor(TEMPERATURE), 
            data=adult, 
            fmt = "%.0f")
```

### 1-months

```{r}
datasummary(Factor(POPULATION) ~ Factor(TEMPERATURE), 
            data=m1_df, 
            fmt = "%.0f")
```

### 2-months

```{r}
datasummary(Factor(POPULATION) ~ Factor(TEMPERATURE), 
            data=m2_df, 
            fmt = "%.0f")
```

### 2.5-months

```{r}
datasummary(Factor(POPULATION) ~ Factor(TEMPERATURE), 
            data=m2.5_df, 
            fmt = "%.0f")
```

###  {.unnumbered}

## mass {.tabset}

### Adults

```{r}
datasummary(Factor(TEMPERATURE) ~ MASS * (NUnique + mean + median + min + max + sd + Histogram), 
            data = drop_na(adult, MASS),  
            fmt = "%.2f")
```

### 1-months

```{r}
datasummary(Factor(TEMPERATURE) ~ MEDIAN_MASS * (NUnique + mean + median + min + max + sd + Histogram), 
            data = drop_na(m1_df, MEDIAN_MASS),  
            fmt = "%.2f")
```

### 2-months

```{r}
datasummary(Factor(TEMPERATURE) ~ MEDIAN_MASS * (NUnique + mean + median + min + max + sd + Histogram), 
            data = drop_na(m2_df, MEDIAN_MASS),  
            fmt = "%.2f")
```

### 2.5-months

```{r}
datasummary(Factor(TEMPERATURE) ~ MEDIAN_MASS * (NUnique + mean + median + min + max + sd + Histogram), 
            data = drop_na(m2.5_df, MEDIAN_MASS),  
            fmt = "%.2f")
```

###  {.unnumbered}

##  {.unnumbered}

# Fit models [random factors] {.tabset}

## 1-month

```{r}
modelNULL <- glmmTMB(MEDIAN_MASS ~ 1, 
                  family=gaussian(),
                  data =m1_df)

model2 <- glmmTMB(MEDIAN_MASS ~ (1|LEVEL), 
                  family=gaussian(),
                  data = m1_df)

model3 <- glmmTMB(MEDIAN_MASS ~ (1|CLUTCH_ORDER), 
                  family=gaussian(),
                  data = m1_df)

model4 <- glmmTMB(MEDIAN_MASS ~ (1|REGION), 
                  family=gaussian(),
                  data = m1_df) 

model5 <- glmmTMB(MEDIAN_MASS ~ (1|REGION) + (1|POPULATION), 
                  family=gaussian(),
                  data = m1_df) 

model6 <- glmmTMB(MEDIAN_MASS ~ (1|CLUTCH_ORDER) + (1|REGION) + (1|POPULATION), 
                  family=gaussian(),
                  data = m1_df) 

AIC(modelNULL, model2, model3, model4, model5, model6) 
BIC(modelNULL, model2, model3, model4, model5, model6)
```

## 2-month

```{r}
modelNULL <- glmmTMB(MEDIAN_MASS ~ 1, 
                  family=gaussian(),
                  data =m2_df)

model2 <- glmmTMB(MEDIAN_MASS ~ (1|LEVEL), 
                  family=gaussian(),
                  data = m2_df)

model3 <- glmmTMB(MEDIAN_MASS ~ (1|CLUTCH_ORDER), 
                  family=gaussian(),
                  data = m2_df)

model4 <- glmmTMB(MEDIAN_MASS ~ (1|REGION), 
                  family=gaussian(),
                  data = m2_df) 

model5 <- glmmTMB(MEDIAN_MASS ~ (1|REGION) + (1|POPULATION), 
                  family=gaussian(),
                  data = m2_df) 

model6 <- glmmTMB(MEDIAN_MASS ~ (1|CLUTCH_ORDER) + (1|REGION) + (1|POPULATION), 
                  family=gaussian(),
                  data = m2_df) 

AIC(modelNULL, model2, model3, model4, model5, model6) 
BIC(modelNULL, model2, model3, model4, model5, model6)
```

## 2.5-month

```{r}
modelNULL <- glmmTMB(MEDIAN_MASS ~ 1, 
                  family=gaussian(),
                  data =m2.5_df)

model2 <- glmmTMB(MEDIAN_MASS ~ (1|LEVEL), 
                  family=gaussian(),
                  data = m2.5_df)

model3 <- glmmTMB(MEDIAN_MASS ~ (1|CLUTCH_ORDER), 
                  family=gaussian(),
                  data = m2.5_df)

model4 <- glmmTMB(MEDIAN_MASS ~ (1|REGION), 
                  family=gaussian(),
                  data = m2.5_df) 

model5 <- glmmTMB(MEDIAN_MASS ~ (1|REGION) + (1|POPULATION), 
                  family=gaussian(),
                  data = m2.5_df) 

model6 <- glmmTMB(MEDIAN_MASS ~ (1|CLUTCH_ORDER) + (1|REGION) + (1|POPULATION), 
                  family=gaussian(),
                  data = m2.5_df) 

AIC(modelNULL, model2, model3, model4, model5, model6) 
BIC(modelNULL, model2, model3, model4, model5, model6)
```

## {-}

For mass measurements at different time periods, including 1, 2, and 2.5 months the best model is the most simply model (i.e., model1), where the only random factor that is present is **CLUTCH_NUMBER**. 

# Fit model [fixed factors] {.tabset}

Now that we have figured out which random factors will be included within out generalized linear mixed effects model we can start to explore different hypothesese by adding in our fixed factors - covariates. 

Fixed factors that will be included will be those that are essential to answering the initial research question based on heiritability of traits between offspring and parental fish - labelled as **MALE** and **FEMALE** in the dataframe as well as their combined score **MIDPOINT**, if applicable. **TEMPERATURE** is also essential to answering the main research question that looks to see if heritability changes at different temperatures. 

Our main research hypothesis will be modelled using the formula below" 
```{r eval=FALSE, echo=TRUE}
MEDIAN_MASS ~ scale(MASS_MALE)*TEMPERATURE
```

An alternative research hypothesis will will test will include an interaction with **PARENTAL_DAYS_IN_TEMPERATURE** to see if heritability was affect by how long adults spent at experimental temperatures. This model may look something like: 

```{r eval=FALSE, echo=TRUE}
MEDIAN_MASS ~ scale(MASS_MALE)*TEMPERATURE:PARENTAL_DAYS_IN_TREATMENT
```

Lets start fitting models: 

## offspring-male {.tabset}

### 1-month

#### Models
##### Main hypothesis
```{r}
model1a <- glmmTMB(MEDIAN_MASS ~ scale(MASS_MALE)*TEMPERATURE+ scale(DENSITY), 
                    family='gaussian', 
                    data=m1_df)
```

##### Alternative hypothesis 
```{r}
model1b <- glmmTMB(MEDIAN_MASS ~ scale(MASS_MALE)*TEMPERATURE*scale(as.numeric(PARENTAL_DAYS_IN_TREATMENT))+ scale(DENSITY), 
                    family='gaussian', 
                    data=m1_df)
```

#### Model selection 
```{r}
AIC(model1a, model1b, k=12) 
BIC(model1a, model1b)
```

Model1a was selected as the best model and will be used going forward.  

#### Model validation {.tabset}
##### DHARMa
```{r}
model1a |> 
  simulateResiduals(plot=TRUE)  

model1a |> testResiduals(plot=T) 
```

##### performance 
```{r fig.width=10, fig.height=14}
model1a |> 
  check_model(detrend=FALSE)
```

##### {-}

#### Partial effect plots 

```{r}
model1a |> ggemmeans(~MASS_MALE|TEMPERATURE) |> 
  plot(add.data =FALSE) 

model1a |> ggemmeans(~TEMPERATURE) |> 
  plot(add.data =FALSE) 
```

#### Model investigation {.tabset}

##### Summary 
```{r}
model1a |> summary()
```

##### Anova 
```{r}
model1a |> Anova()
```

##### Confint 
```{r}
model1a |> confint()
```

##### r-squared 
```{r}
model1a |> r2_nakagawa()
```

##### {-} 

#### Summary figure 
```{r}
m1.mass <- emmeans(model1a, ~ MASS_MALE*TEMPERATURE, 
                 at =list(MASS_MALE=seq(from =min(m1_df$MASS_MALE), to =max(m1_df$MASS_MALE), by=.25)))

m1.mass.df <- as.data.frame(m1.mass)

m1.mass.obs <- drop_na(m1_df, MASS_MALE, MEDIAN_MASS) |> 
  mutate(Pred =predict(model1a, re.form=NA, type ='response'), 
         Resid =residuals(model1a, type ='response'), 
         Fit =Pred+Resid) 

m1.mass.obs.summarize <-  m1.mass.obs |> 
  group_by(CLUTCH_NUMBER, TEMPERATURE) |> 
  summarise(mean.mass =mean(Fit, na.rm=TRUE), 
            mean.mass.male =mean(MASS_MALE, na.rm = TRUE), 
            sd.mass =sd(Fit, na.rm =TRUE), 
            n.mass = n()) |> 
  mutate(se.mass = sd.mass / sqrt(n.mass), 
         lower.ci.mass =mean.mass - qt(1-(0.05/2), n.mass -1) * se.mass, 
         upper.ci.mass =mean.mass + qt(1-(0.05/2), n.mass -1) * se.mass) |> 
  ungroup()

ggplot(data = m1.mass.df, aes(x=MASS_MALE, y=emmean)) + 
  stat_smooth(aes(color=TEMPERATURE), 
              method = "lm") + 
  geom_pointrange(data = m1.mass.obs.summarize, aes(x =mean.mass.male, 
                                                  y =mean.mass, 
                                                  ymin =lower.ci.mass, 
                                                  ymax =upper.ci.mass, 
                                                  color = TEMPERATURE)) +  
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  scale_fill_manual(values =c("#69d7d8","#ff9c56", "#903146")) +
  facet_wrap(~TEMPERATURE)+
  xlab("PARENTAL MALE MASS (g)") + 
  ylab("OFFSPRING MASS (g)") + 
  ggtitle("Offspring-male relationship") +
  theme_classic()
```

### 2-month

#### Models
##### Main hypothesis
```{r}
model1a <- glmmTMB(MEDIAN_MASS ~ scale(MASS_MALE)*TEMPERATURE+ scale(DENSITY), 
                    family=gaussian(), 
                    data=m2_df)
```

##### Alternative hypothesis 
```{r}
model1b <- glmmTMB(MEDIAN_MASS ~ scale(MASS_MALE)*TEMPERATURE*scale(as.numeric(PARENTAL_DAYS_IN_TREATMENT))+ scale(DENSITY), 
                    family=gaussian(), 
                    data=m2_df)
```

#### Model selection 
```{r}
AIC(model1a, model1b, k=12) 
BIC(model1a, model1b)
```

The null model appears better than the models that we used. Let's explore the data bit more and see if we can find a reason for this. Let's start by looking at a basic histogram of our data. 

```{r}
hist(m2_df$MEDIAN_MASS)
```

There appears to be a left skew within our data. Let's see if this can be better modelled with a Gamma distribution. If not we can try to incorporate transformations to our response variable. The model validations below also could use some improving. 

#### Model validation {.tabset}
##### DHARMa
```{r}
model1a |> 
  simulateResiduals(plot=TRUE)  

model1a |> testResiduals(plot=T) 
```

##### performance 
```{r fig.width=10, fig.height=14}
model1a |> 
  check_model(detrend=FALSE)
```

##### {-}

#### Partial effect plots 

```{r}
model1a |> ggemmeans(~MASS_MALE|TEMPERATURE) |> 
  plot(add.data =FALSE) 

model1a |> ggemmeans(~TEMPERATURE) |> 
  plot(add.data =FALSE) 
```

#### Model investigation {.tabset}

##### Summary 
```{r}
model1a |> summary()
```

##### Anova 
```{r}
model1a |> Anova()
```

##### Confint 
```{r}
model1a |> confint()
```

##### r-squared 
```{r}
model1a |> r2_nakagawa()
```

##### {-} 

#### Summary figure 
```{r}
m2.mass <- emmeans(model1a, ~ MASS_MALE*TEMPERATURE, 
                 at =list(MASS_MALE=seq(from =min(m2_df$MASS_MALE), to =max(m2_df$MASS_MALE), by=.25)))

m2.mass.df <- as.data.frame(m2.mass)

m2.mass.obs <- drop_na(m2_df, MASS_MALE, MEDIAN_MASS) |> 
  mutate(Pred =predict(model1a, re.form=NA, type ='response'), 
         Resid =residuals(model1a, type ='response'), 
         Fit =Pred+Resid) 

m2.mass.obs.summarize <-  m2.mass.obs |> 
  group_by(CLUTCH_NUMBER, TEMPERATURE) |> 
  summarise(mean.mass =mean(Fit, na.rm=TRUE), 
            mean.mass.male =mean(MASS_MALE, na.rm = TRUE), 
            sd.mass =sd(Fit, na.rm =TRUE), 
            n.mass = n()) |> 
  mutate(se.mass = sd.mass / sqrt(n.mass), 
         lower.ci.mass =mean.mass - qt(1-(0.05/2), n.mass -1) * se.mass, 
         upper.ci.mass =mean.mass + qt(1-(0.05/2), n.mass -1) * se.mass) |> 
  ungroup()

ggplot(data = m2.mass.df, aes(x=MASS_MALE, y=emmean)) + 
  stat_smooth(aes(color=TEMPERATURE), 
              method = "lm", 
              formula = y ~ x) + 
  geom_pointrange(data = m2.mass.obs.summarize, aes(x =mean.mass.male, 
                                                  y =mean.mass, 
                                                  ymin =lower.ci.mass, 
                                                  ymax =upper.ci.mass, 
                                                  color = TEMPERATURE)) +  
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  scale_fill_manual(values =c("#69d7d8","#ff9c56", "#903146")) +
  facet_wrap(~TEMPERATURE)+
  xlab("PARENTAL MALE STANDARD LENGTH (mm)") + 
  ylab("OFFSPRING STANDARD LENGTH (mm)") + 
  ggtitle("Offspring-male relationship") +
  theme_classic()
```

### 2.5-month

#### Models
##### Main hypothesis
```{r}
model1a <- glmmTMB(MEDIAN_MASS ~ scale(MASS_MALE)*TEMPERATURE+ scale(DENSITY), 
                    family=gaussian(link ="identity"), 
                    data=m2.5_df)
```

##### Alternative hypothesis 
```{r}
model1b <- glmmTMB(MEDIAN_MASS ~ scale(MASS_MALE)*TEMPERATURE*scale(as.numeric(PARENTAL_DAYS_IN_TREATMENT))+ scale(DENSITY), 
                    family=gaussian(link ="identity"), 
                    data=m2.5_df)
```

#### Model selection 
```{r}
AIC(model1a, model1b, k=13) 
BIC(model1a, model1b)
```

Once again the **NULL** model seems to outperform our hypothesis testing models. Let's follow the steps that we conducted for 2-month data and appy a log transformation to our dataset to see if it improved the model. 

#### Model validation {.tabset}
##### DHARMa
```{r}
model1a |> 
  simulateResiduals(plot=TRUE)  

model1a |> testResiduals(plot=T) 
```

##### performance 
```{r fig.width=10, fig.height=14}
model1a |> 
  check_model(detrend=FALSE)
```

##### {-}

#### Partial effect plots 

```{r}
model1a |> ggemmeans(~MASS_MALE|TEMPERATURE) |> 
  plot(add.data =FALSE) 

model1a |> ggemmeans(~TEMPERATURE) |> 
  plot(add.data =FALSE) 
```

#### Model investigation {.tabset}

##### Summary 
```{r}
model1a |> summary()
```

##### Anova 
```{r}
model1a |> Anova()
```

##### Confint 
```{r}
model1a |> confint()
```

##### r-squared 
```{r}
model1a |> r2_nakagawa()
```

##### {-} 

#### Summary figure 
```{r}
m1.mass <- emmeans(model1a, ~ MASS_MALE*TEMPERATURE, 
                 at =list(MASS_MALE=seq(from =min(m2.5_df$MASS_MALE), to =max(m2.5_df$MASS_MALE), by=.25)))

m1.mass.df <- as.data.frame(m1.mass)

m1.mass.obs <- drop_na(m2.5_df, MASS_MALE, MEDIAN_MASS) |> 
  mutate(Pred =predict(model1a, re.form=NA, type ='response'), 
         Resid =residuals(model1a, type ='response'), 
         Fit =Pred+Resid) 

m1.mass.obs.summarize <-  m1.mass.obs |> 
  group_by(CLUTCH_NUMBER, TEMPERATURE) |> 
  summarise(mean.mass =mean(Fit, na.rm=TRUE), 
            mean.mass.male =mean(MASS_MALE, na.rm = TRUE), 
            sd.mass =sd(Fit, na.rm =TRUE), 
            n.mass = n()) |> 
  mutate(se.mass = sd.mass / sqrt(n.mass), 
         lower.ci.mass =mean.mass - qt(1-(0.05/2), n.mass -1) * se.mass, 
         upper.ci.mass =mean.mass + qt(1-(0.05/2), n.mass -1) * se.mass) |> 
  ungroup()

ggplot(data = m1.mass.df, aes(x=MASS_MALE, y=emmean)) + 
  stat_smooth(aes(color=TEMPERATURE), 
              method = "lm", 
              formula = y ~ x) + 
  geom_pointrange(data = m1.mass.obs.summarize, aes(x =mean.mass.male, 
                                                  y =mean.mass, 
                                                  ymin =lower.ci.mass, 
                                                  ymax =upper.ci.mass, 
                                                  color = TEMPERATURE)) +  
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  scale_fill_manual(values =c("#69d7d8","#ff9c56", "#903146")) +
  facet_wrap(~TEMPERATURE)+
  xlab("PARENTAL MALE MASS (g)") + 
  ylab("MEDIAN MASS (g)") + 
  ggtitle("Offspring-male relationship") +
  theme_classic()
```

### {-}

## Offspring-Midpoint {.tabset}

### 1-month

#### Models
##### Main hypothesis
```{r}
model1a <- glmmTMB(MEDIAN_MASS ~ scale(MASS_MIDPOINT)*TEMPERATURE + scale(DENSITY), 
                    family=gaussian(), 
                    data=m1_df)
```

##### Alternative hypothesis 
```{r}
model1b <- glmmTMB(MEDIAN_MASS ~ scale(MASS_MIDPOINT)*TEMPERATURE*scale(as.numeric(PARENTAL_DAYS_IN_TREATMENT)) + scale(DENSITY), 
                    family=gaussian(), 
                    data=m1_df)
```

#### Model selection 
```{r}
AIC(model1a, model1b, k=12) 
BIC(model1a, model1b)
```

Model1a was selected as the best model and will be used going forward.  

#### Model validation {.tabset}
##### DHARMa
```{r}
model1a |> 
  simulateResiduals(plot=TRUE)  

model1a |> testResiduals(plot=T) 
```

##### performance 
```{r fig.width=10, fig.height=14}
model1a |> 
  check_model(detrend=FALSE)
```

##### {-}

#### Partial effect plots 

```{r}
model1a |> ggemmeans(~MASS_MIDPOINT|TEMPERATURE) |> 
  plot(add.data =FALSE) 

model1a |> ggemmeans(~TEMPERATURE) |> 
  plot(add.data =FALSE) 
```

#### Model investigation {.tabset}

##### Summary 
```{r}
model1a |> summary()
```

##### Anova 
```{r}
model1a |> Anova()
```

##### Confint 
```{r}
model1a |> confint()
```

##### r-squared 
```{r}
model1a |> r2_nakagawa()
```

##### {-} 

#### Summary figure 
```{r}
m1_df <-  
  m1_df |> 
  drop_na(MASS_MIDPOINT)

m1.mass <- emmeans(model1a, ~ MASS_MIDPOINT*TEMPERATURE, 
                 at =list(MASS_MIDPOINT=seq(from =min(m1_df$MASS_MIDPOINT), to =max(m1_df$MASS_MIDPOINT), by=.25)))

m1.mass.df <- as.data.frame(m1.mass)

m1.mass.obs <- drop_na(m1_df, MASS_MIDPOINT, MEDIAN_MASS) |> 
  mutate(Pred =predict(model1a, re.form=NA, type ='response'), 
         Resid =residuals(model1a, type ='response'), 
         Fit =Pred+Resid) 

m1.mass.obs.summarize <-  m1.mass.obs |> 
  group_by(CLUTCH_NUMBER, TEMPERATURE) |> 
  summarise(mean.mass =mean(Fit, na.rm=TRUE), 
            mean.mass.female =mean(MASS_MIDPOINT, na.rm = TRUE), 
            sd.mass =sd(Fit, na.rm =TRUE), 
            n.mass = n()) |> 
  mutate(se.mass = sd.mass / sqrt(n.mass), 
         lower.ci.mass =mean.mass - qt(1-(0.05/2), n.mass -1) * se.mass, 
         upper.ci.mass =mean.mass + qt(1-(0.05/2), n.mass -1) * se.mass) |> 
  ungroup()

ggplot(data = m1.mass.df, aes(x=MASS_MIDPOINT, y=emmean)) + 
  stat_smooth(aes(color=TEMPERATURE), 
              method = "lm") + 
  geom_pointrange(data = m1.mass.obs.summarize, aes(x =mean.mass.female, 
                                                  y =mean.mass, 
                                                  ymin =lower.ci.mass, 
                                                  ymax =upper.ci.mass, 
                                                  color = TEMPERATURE)) +  
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  scale_fill_manual(values =c("#69d7d8","#ff9c56", "#903146")) +
  facet_wrap(~TEMPERATURE)+
  xlab("PARENTAL MIDPOINT STANDARD LENGTH (mm)") + 
  ylab("OFFSPRING STANDARD LENGTH (mm)") + 
  ggtitle("Offspring-male relationship") +
  theme_classic()
```

### 2-month

#### Models
##### Main hypothesis
```{r}
model1a <- glmmTMB(MEDIAN_MASS ~ scale(MASS_MIDPOINT)*TEMPERATURE + scale(DENSITY), 
                    family=gaussian(), 
                    data=m2_df)
```

##### Alternative hypothesis 
```{r}
model1b <- glmmTMB(MEDIAN_MASS ~ scale(MASS_MIDPOINT)*TEMPERATURE*scale(as.numeric(PARENTAL_DAYS_IN_TREATMENT)) + scale(DENSITY),
                    family=gaussian(), 
                    data=m2_df)
```

#### Model selection 
```{r}
AIC(model1a, model1b, k=12) 
BIC(model1a, model1b)
```

#### Model validation {.tabset}
##### DHARMa
```{r}
model1a |> 
  simulateResiduals(plot=TRUE)  

model1a |> testResiduals(plot=T) 
```

##### performance 
```{r fig.width=10, fig.height=14}
model1a |> 
  check_model(detrend=FALSE)
```

##### {-}


#### Model validation {.tabset}
##### DHARMa
```{r}
model1a |> 
  simulateResiduals(plot=TRUE)  

model1a |> testResiduals(plot=T) 
```

##### performance 
```{r fig.width=10, fig.height=14}
model1a |> 
  check_model(detrend=FALSE)
```

##### {-}

#### Partial effect plots 

```{r}
model1a |> ggemmeans(~MASS_MIDPOINT|TEMPERATURE) |> 
  plot(add.data =FALSE) 

model1a |> ggemmeans(~TEMPERATURE) |> 
  plot(add.data =FALSE) 
```

#### Model investigation {.tabset}

##### Summary 
```{r}
model1a |> summary()
```

##### Anova 
```{r}
model1a |> Anova()
```

##### Confint 
```{r}
model1a |> confint()
```

##### r-squared 
```{r}
model1a |> r2_nakagawa()
```

##### {-} 

#### Summary figure 
```{r}
m2_df <-  
  m2_df |> 
  drop_na(MASS_MIDPOINT)
m2.mass <- emmeans(model1a, ~ MASS_MIDPOINT*TEMPERATURE, 
                 at =list(MASS_MIDPOINT=seq(from =min(m2_df$MASS_MIDPOINT), to =max(m2_df$MASS_MIDPOINT), by=.25)))

m2.mass.df <- as.data.frame(m2.mass)

m2.mass.obs <- drop_na(m2_df, MASS_MIDPOINT,MEDIAN_MASS) |> 
  mutate(Pred =predict(model1a, re.form=NA, type ='response'), 
         Resid =residuals(model1a, type ='response'), 
         Fit =Pred+Resid) 

m2.mass.obs.summarize <-  m2.mass.obs |> 
  group_by(CLUTCH_NUMBER, TEMPERATURE) |> 
  summarise(mean.mass =mean(Fit, na.rm=TRUE), 
            mean.mass.male =mean(MASS_MIDPOINT, na.rm = TRUE), 
            sd.mass =sd(Fit, na.rm =TRUE), 
            n.mass = n()) |> 
  mutate(se.mass = sd.mass / sqrt(n.mass), 
         lower.ci.mass =mean.mass - qt(1-(0.05/2), n.mass -1) * se.mass, 
         upper.ci.mass =mean.mass + qt(1-(0.05/2), n.mass -1) * se.mass) |> 
  ungroup()

ggplot(data = m2.mass.df, aes(x=MASS_MIDPOINT, y=emmean)) + 
  stat_smooth(aes(color=TEMPERATURE), 
              method = "lm", 
              formula = y ~ x) + 
  geom_pointrange(data = m2.mass.obs.summarize, aes(x =mean.mass.male, 
                                                  y =mean.mass, 
                                                  ymin =lower.ci.mass, 
                                                  ymax =upper.ci.mass, 
                                                  color = TEMPERATURE)) +  
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  scale_fill_manual(values =c("#69d7d8","#ff9c56", "#903146")) +
  facet_wrap(~TEMPERATURE)+
  xlab("PARENTAL MIDPOINT STANDARD LENGTH (mm)") + 
  ylab("OFFSPRING STANDARD LENGTH (mm)") + 
  ggtitle("Offspring-male relationship") +
  theme_classic()
```

### 2.5-month

#### Models
##### Main hypothesis
```{r}
model1a <- glmmTMB(MEDIAN_MASS ~ scale(MASS_MIDPOINT)*TEMPERATURE + scale(DENSITY), 
                    family=gaussian(link ="identity"), 
                    data=m2.5_df)
```

##### Alternative hypothesis 
```{r}
model1b <- glmmTMB(MEDIAN_MASS ~ MASS_MIDPOINT*TEMPERATURE*as.numeric(PARENTAL_DAYS_IN_TREATMENT) + scale(DENSITY), 
                    family=gaussian(link ="identity"), 
                    data=m2.5_df)
```

#### Model selection 
```{r}
AIC(model1a, model1b, k=12) 
BIC(model1a, model1b)
```

Once again the **NULL** model seems to outperform our hypothesis testing models. Let's follow the steps that we conducted for 2-month data and appy a log transformation to our dataset to see if it improved the model. 


#### Model validation {.tabset}
##### DHARMa
```{r}
model1a |> 
  simulateResiduals(plot=TRUE)  

model1a |> testResiduals(plot=T) 
```

##### performance 
```{r fig.width=10, fig.height=14}
model1a |> 
  check_model(detrend=FALSE)
```

##### {-}

#### Partial effect plots 

```{r}
model1a |> ggemmeans(~MASS_MIDPOINT|TEMPERATURE) |> 
  plot(add.data =FALSE) 

model1a |> ggemmeans(~TEMPERATURE) |> 
  plot(add.data =FALSE) 
```

#### Model investigation {.tabset}

##### Summary 
```{r}
model1a |> summary()
```

##### Anova 
```{r}
model1a |> Anova()
```

##### Confint 
```{r}
model1a |> confint()
```

##### r-squared 
```{r}
model1a |> r2_nakagawa()
```

##### {-} 

#### Summary figure 
```{r}
m2.5_df <- m2.5_df |> 
  drop_na(MASS_MIDPOINT)
m2.5.mass <- emmeans(model1a, ~ MASS_MIDPOINT*TEMPERATURE, 
                 at =list(MASS_MIDPOINT=seq(from =min(m2.5_df$MASS_MIDPOINT), to =max(m2.5_df$MASS_MIDPOINT), by=.25)))

m2.5.mass.df <- as.data.frame(m2.5.mass)

m2.5.mass.obs <- drop_na(m2.5_df, MASS_MIDPOINT, MEDIAN_MASS) |> 
  mutate(Pred =predict(model1a, re.form=NA, type ='response'), 
         Resid =residuals(model1a, type ='response'), 
         Fit =Pred+Resid) 

m2.5.mass.obs.summarize <-  m2.5.mass.obs |> 
  group_by(CLUTCH_NUMBER, TEMPERATURE) |> 
  summarise(mean.mass =mean(Fit, na.rm=TRUE), 
            mean.mass.male =mean(MASS_MIDPOINT, na.rm = TRUE), 
            sd.mass =sd(Fit, na.rm =TRUE), 
            n.mass = n()) |> 
  mutate(se.mass = sd.mass / sqrt(n.mass), 
         lower.ci.mass =mean.mass - qt(1-(0.05/2), n.mass -1) * se.mass, 
         upper.ci.mass =mean.mass + qt(1-(0.05/2), n.mass -1) * se.mass) |> 
  ungroup()

ggplot(data = m2.5.mass.df, aes(x=MASS_MIDPOINT, y=emmean)) + 
  stat_smooth(aes(color=TEMPERATURE), 
              method = "lm", 
              formula = y ~ x) + 
  geom_pointrange(data = m2.5.mass.obs.summarize, aes(x =mean.mass.male, 
                                                  y =mean.mass, 
                                                  ymin =lower.ci.mass, 
                                                  ymax =upper.ci.mass, 
                                                  color = TEMPERATURE)) +  
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  scale_fill_manual(values =c("#69d7d8","#ff9c56", "#903146")) +
  facet_wrap(~TEMPERATURE)+
  xlab("PARENTAL MALE STANDARD LENGTH (mm)") + 
  ylab("OFFSPRING STANDARD LENGTH (mm)") + 
  ggtitle("Offspring-male relationship") +
  theme_classic()
```

### {-} 

## {-}
