---
title: '02E.OxygenUptake: Resting'
author: "Elliott Schmidt"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true  
    toc_depth: 2
    toc_float: true
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    highlight: monochrome
    theme: cerulean
    latex_engine: xelatex
---

# Load libraries

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse) # data manipulation
library(ggpubr) # producing data exploratory plots
library(modelsummary) # descriptive data 
library(glmmTMB) # running generalised mixed models 
library(DHARMa) # model diagnostics 
library(performance) # model diagnostics  
library(ggeffects) # partial effect plots 
library(car) # running Anova on model 
library(emmeans) # post-hoc analysis 
library(patchwork) # image formatting
```

# Import data

```{r import-adults, warning=FALSE, message=FALSE}
df_adults <- read_csv("import_data/resp_results_adults2.csv")
df_jresp <- read_csv("import_data/resp_results_juveniles.csv")
```

# Data manipulation

## Adults

```{r data-manipulation-1}
df_adults_cleaned <- df_adults |> 
  mutate(FISH_ID = factor(FISH_ID), 
         Sex = factor(Sex), 
         Population = factor(Population), 
         Tank = factor(Tank), 
         Chamber = factor(Chamber), 
         System =factor(System), 
         Temperature =factor(Temperature), 
         True_resting=factor(True_resting)) 

df_males <- df_adults_cleaned |> 
  filter(Sex == "M")
df_females <- df_adults_cleaned |> 
  filter(Sex == "F")

df_adults_cleaned2 <- df_males |> 
  full_join(select(df_females, c("Tank","Temperature","Mass","Resting","Max","AAS","FISH_ID","Sex")), by="Tank") |> 
  mutate(Temperature.x = coalesce(Temperature.x, Temperature.y), 
         FISH_ID.x = coalesce(FISH_ID.x, FISH_ID.y),
         Sex.x = coalesce(Sex.x, Sex.y),
         Resting.x =coalesce(Resting.x, Resting.y), 
         Mass.x =coalesce(Mass.x,Mass.y)) |>  
  drop_na(Resting.x)
```

## Juveniles

```{r data-manipulation-2}
df_jresp$Population <-  fct_collapse(df_jresp$Population, 
                                      `Vlassof cay`= c("Vlassof reef", "Vlassof", "Vlassof Cay", "Vlassof cay"), 
                                      `Arlington reef` = c("Arlington reef","Arlginton reef")) 

#df_jresp$Female <-  fct_collapse(df_jresp$Female, 
                                  #`CARL359`= c("CARL359", "CARL59")) 


df_jresp2 <-  df_jresp |> 
  unite("F0", c("Male","Female"), sep="_", remove=FALSE) |>
  mutate(across(1:7, factor), 
         Temperature = factor(Temperature), 
         True_resting = factor(True_resting)) 

#df_jresp2_rest <- df_jresp2 |> 
  #filter(True_resting == "Y")
```

## Merging dataframes

```{r data-manipulation-3.0}
temp1a <- df_jresp2 |> 
  mutate(FISH_ID.x = Male)
temp1b <- df_jresp2 |> 
  mutate(FISH_ID.y = Female)
```

```{r data-manipulation-3.1}
temp2a <- temp1a |> 
  left_join(select(df_adults_cleaned2, c("FISH_ID.x",
                                          "Sex.x",
                                          "Resting.x", 
                                          "Max.x", 
                                          "AAS.x", 
                                          "Mass.x")), 
                    by="FISH_ID.x")
```

```{r data-manipulation-3.2}
temp2b <- temp1b |> 
  left_join(select(df_adults_cleaned2, c("FISH_ID.y",
                            "Sex.y",
                            "Resting.y", 
                            "Max.y", 
                            "AAS.y", 
                            "Mass.y")), 
                   by="FISH_ID.y") 
```

```{r data-manipulation-3.3}
df_merged <- temp2a |> 
  left_join(select(temp2b, c("Clutch","Replicate", 
                             "FISH_ID.y",
                             "Resting.y", 
                             "Max.y", 
                             "AAS.y", 
                             "Mass.y")), 
            by=c("Clutch","Replicate"))
```

```{r data-manipulation-3.4}
df <- df_merged |> 
  mutate(Resting_MALE =Resting.x, 
         Max_MALE =Max.x, 
         AAS_MALE =AAS.x, 
         Mass_MALE =Mass.x, 
         FISH_ID.y =FISH_ID.x,#makes more sense for males to be .y instead of .x
         FISH_ID.x =FISH_ID.x, 
         Resting_FEMALE =Resting.y, 
         Max_FEMALE =Max.y, 
         AAS_FEMALE =AAS.y, 
         Mass_FEMALE =Mass.y) |>  
  mutate(Resting_MALE = Resting_MALE/Mass_MALE, 
         Resting_FEMALE =Resting_FEMALE/Mass_FEMALE) |>
  mutate(Resting_MID =(Resting_MALE+Resting_FEMALE)/2) |> # easier to do it again
  filter(True_resting == "Y") |> # this should remove 10 individuals from the df
  mutate(Resting_MID =coalesce(Resting_MID, Resting_MALE)) |> 
  mutate(Resting_MID =coalesce(Resting_MID, Resting_FEMALE)) |> 
  unite("ChbSys", Chamber:System, remove=FALSE) |>
  mutate(ChbSys =factor(ChbSys)) |>
  drop_na(Resting) |> 
  filter(Resting < 0.5) |>
  group_by(Clutch) |> 
  mutate(MEDIAN_Resting =median(Resting_kg_wet)) |> 
  ungroup() 
  #select(-c(Replicate, Chamber, System, Volume, Date_tested, Swim, Mass, Dry_mass, 18:26)) |> 
  #distinct() |> 
  #drop_na(Resting_MID)
```

# Exploratory analysis 

## Offspring-Male

```{r eda-male, warning=FALSE, message=FALSE, fig.width=4, fig.height=3}
plot1 <- ggplot(df, aes(x=Resting_MALE, y=Resting, color=Temperature)) + 
  stat_smooth(method = "lm") +
  #geom_point(alpha=0.1) + 
  ggtitle("Offspring-male relationship") + 
  xlab("Resting (offspring)") + 
  ylab("Resting (parental)") +
  theme_classic() + 
  theme(legend.position = "bottom"); plot1
``` 

# Models

## Random factors
```{r}
modelNULL <- glmmTMB(Resting ~ 1, 
                  family=gaussian(),
                  data =df)

model1 <- glmmTMB(Resting ~ (1|Male), 
                  family=gaussian(),
                  data = df)

model2 <- glmmTMB(Resting ~ (1|Male) + (1|ChbSys), 
                  family=gaussian(),
                  data = df) 



AIC(modelNULL, model1, model2, k=3) 
BIC(modelNULL, model1, model2)
```

## Main hypothesis

```{r}
model1a <- glmmTMB(Resting ~ scale(as.numeric(Resting.x), center=TRUE)*Temperature + scale(Mass, center=TRUE) + (1| Male) + (1|ChbSys),    
                   family=gaussian(),
                   data=df)
```

# Model validation {.tabset}

## DHARMa

```{r}
model1a |> 
  simulateResiduals(plot=TRUE)  

model1a |> testResiduals(plot=T)  
```

## performance 
```{r}
check_model(model1a, detrend =FALSE)
``` 

## {-} 

# Partial effect plots

```{r warning=FALSE, message=FALSE}
model1a |> ggemmeans(~Resting.x|Temperature) |> 
  plot(add.data =TRUE) 

model1a |> ggemmeans(~Temperature) |> 
  plot(add.data =TRUE)

model1a |> ggemmeans(~Mass) |> 
  plot(add.data =TRUE)
```

Model investigation {.tabset}

## Summary

```{r}
model1a |> summary()
```

## Anova

```{r}
model1a |> Anova()
```

## Confint

```{r}
model1a |> confint()
```

## r-squared

```{r}
model1a |> r2_nakagawa()
```

# Post-hoc 

```{r}
model1a |> emmeans(~Temperature) 
model1a |> emmeans(~Temperature) |> pairs()|> summary(adjust="tukey")
```

# Summary figure

```{r fig.height = 8, fig.width=12, warning=FALSE} 
df <- df |> drop_na(Resting, Resting.x, Mass)
m3.resting <- emmeans(model1a, ~ Resting.x*Temperature, 
                 at =list(Resting.x=seq(from =min(df$Resting.x), to =max(df$Resting.x), by=.1)))

m3.resting.df <- as.data.frame(m3.resting)

m3.resting.obs <- df |> 
  mutate(Pred =predict(model1a, re.form=NA, type ='response'), 
         Resid =residuals(model1a, type ='response'), 
         Fit =Pred+Resid) 

m3.resting.obs.summarize <-  m3.resting.obs |> 
  group_by(Male, Temperature) |> 
  summarise(mean.resting =mean(Fit, na.rm=TRUE), 
            mean.resting.male =mean(Resting.x, na.rm = TRUE), 
            sd.resting =sd(Fit, na.rm =TRUE), 
            n.resting = n()) |> 
  mutate(se.resting = sd.resting / sqrt(n.resting), 
         lower.ci.resting =mean.resting - qt(1-(0.05/2), n.resting -1) * se.resting, 
         upper.ci.resting =mean.resting + qt(1-(0.05/2), n.resting -1) * se.resting) |> 
  ungroup()

m3.plot <- ggplot(data = m3.resting.df, aes(x=Resting.x, y=emmean)) + 
  stat_smooth(aes(color=Temperature), 
              method = "lm") + 
  geom_ribbon(aes(ymin=lower.CL, ymax=upper.CL, fill=Temperature), alpha=0.5) +
  geom_pointrange(data = m3.resting.obs.summarize, aes(x =mean.resting.male, 
                                                  y =mean.resting, 
                                                  ymin =lower.ci.resting, 
                                                  ymax =upper.ci.resting, 
                                                  color = Temperature)) +  
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  scale_fill_manual(values =c("#69d7d8","#ff9c56", "#903146")) +
  facet_wrap(~Temperature)+
  scale_y_continuous(limits = c(0,0.5), breaks = seq(0,0.5,by=0.1))+
  xlab("PARENTAL MALE STANDARD LENGTH (mm)") + 
  ylab("OFFSPRING STANDARD LENGTH (mm)") + 
  ggtitle("Offspring-male relationship") +
  theme_classic()+theme(legend.position = 'none'); m3.plot

m3.density <- ggdensity(m3.resting.obs, x="Fit", 
          color = "Temperature", 
          fill = "Temperature", 
          rug=TRUE, 
          add="median", 
          alpha=0.5,
          palette=c("#69d7d8","#ff9c56", "#903146")) + 
  scale_x_continuous(limits = c(0,0.5), breaks = seq(0,0.5,by=0.1))+
          clean_theme() + rotate() + 
  theme(legend.position = c(0.7,0.9), 
                                legend.box.background = element_rect(color = "black", size=2))

m3.plot.final <-m3.plot + m3.density + 
  plot_layout(guides = "collect" & theme(legend.position = "bottom"), 
              widths = c(2,1)); m3.plot.final

```

# Slopes

```{r}
add.df <- split(m3.resting.obs.summarize, m3.resting.obs.summarize$Temperature) |> 
  map(~lm(mean.resting ~ mean.resting.male, data=.)) |> 
  map(summary) |> 
  map_dbl("r.squared") |> 
  as.data.frame()

add.df <- add.df |>
  mutate(Temperature = row.names(add.df)) |>
  rename(r.sqaured =names(add.df)[1]) 

sd_values <- df |> group_by(Temperature) |> 
  summarise(sd =sd(Mass), 
            se =sd(Mass)/sqrt(nrow(df)), 
            Lower.CI =mean(Mass) - qt(1-(0.05/2), nrow(df) -1) *se, 
            Upper.CI =mean(Mass) + qt(1-(0.05/2), nrow(df) -1) *se)  

df.results.1 <- m3.resting.obs.summarize |> 
  group_by(Temperature) |> 
  do({ 
    mod = lm(mean.resting ~ mean.resting.male, data = .) 
    data.frame(group = "Resting", 
               slope = coef(mod)[2], 
               Heritability = coef(mod)[2]*2)
    }) |> 
  as.data.frame() |> 
  mutate(Heritability = case_when(Heritability <=0 ~ 0, 
                                  TRUE ~ Heritability)) |> 
  inner_join(add.df, by="Temperature") |> 
  inner_join(sd_values, by="Temperature"); df.results.1
``` 

# Within parental variation 

```{r}
cv_within <- m3.resting.obs |> 
  group_by(Male) |> 
  mutate(mean_value =mean(Fit), 
         sd_value =sd(Fit), 
         CV =(sd_value/mean_value) * 100) |>
  ungroup() |> 
  select(-c("Replicate","Mass","Dry_mass","ChbSys","Chamber","System","Pred","Fit","Resid")) |> 
  distinct(Male, .keep_all=TRUE) 

within_var <- aov(CV ~ Temperature, 
                  data=cv_within) 
summary(within_var) 
```

# Among parental variation
```{r}
cv_among <- cv_within |> 
  group_by(Temperature) |> 
  mutate(mean_among =mean(CV), 
         sd_among =sd(CV), 
         cv_among =(sd_among/mean_among)*100) |> 
  ungroup() |> 
  distinct(cv_among, .keep_all = T) |> 
  select(c("Temperature","cv_among")) |> 
  arrange(Temperature)
cv_among
```