---
title: '02E.OxygenUptake: Maximum'
author: "Elliott Schmidt"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: true  
    toc_depth: 2
    toc_float: true
    code_folding: show
    collapse: no
    df_print: paged
    fig_caption: yes
    fig_height: 4
    fig_width: 6
    highlight: monochrome
    theme: cerulean
    latex_engine: xelatex
---

# Load libraries

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse) # data manipulation
library(ggpubr) # producing data exploratory plots
library(modelsummary) # descriptive data 
library(glmmTMB) # running generalised mixed models 
library(DHARMa) # model diagnostics 
library(performance) # model diagnostics  
library(ggeffects) # partial effect plots 
library(car) # running Anova on model 
library(emmeans) # post-hoc analysis 
library(patchwork) # image formatting
```

# Import data

```{r import-adults, warning=FALSE, message=FALSE}
df_adults <- read_csv("import_data/resp_results_adults2.csv")
df_jresp <- read_csv("import_data/resp_results_juveniles.csv")
``` 

# Data manipulation

## Adults

```{r data-manipulation-1}
df_adults_cleaned <- df_adults |> 
  mutate(FISH_ID = factor(FISH_ID), 
         Sex = factor(Sex), 
         Population = factor(Population), 
         Tank = factor(Tank), 
         Chamber = factor(Chamber), 
         System =factor(System), 
         Temperature =factor(Temperature), 
         True_resting=factor(True_resting)) 

df_males <- df_adults_cleaned |> 
  filter(Sex == "M")
df_females <- df_adults_cleaned |> 
  filter(Sex == "F")

df_adults_cleaned2 <- df_males |> 
  full_join(select(df_females, c("Tank","Temperature","Mass","Resting","Resting_kg","Max","Max_kg","AAS","AAS_kg","FISH_ID","Sex")), by="Tank") |> 
  mutate(Temperature.x = coalesce(Temperature.x, Temperature.y), 
         FISH_ID.x = coalesce(FISH_ID.x, FISH_ID.y),
         Sex.x = coalesce(Sex.x, Sex.y),
         Max.x =coalesce(Max.x, Max.y), 
         Mass.x =coalesce(Mass.x,Mass.y), 
         Max_kg.x =coalesce(Max_kg.x, Max_kg.y)) |>  
  drop_na(Max.x)
```

## Juveniles

```{r data-manipulation-2}
df_jresp$Population <-  fct_collapse(df_jresp$Population, 
                                      `Vlassof cay`= c("Vlassof reef", "Vlassof", "Vlassof Cay", "Vlassof cay"), 
                                      `Arlington reef` = c("Arlington reef","Arlginton reef")) 

#df_jresp$Female <-  fct_collapse(df_jresp$Female, 
                                  #`CARL359`= c("CARL359", "CARL59")) 


df_jresp2 <-  df_jresp |> 
  unite("F0", c("Male","Female"), sep="_", remove=FALSE) |>
  mutate(across(1:7, factor), 
         Temperature = factor(Temperature), 
         True_resting = factor(True_resting)) 

#df_jresp2_rest <- df_jresp2 |> 
  #filter(True_resting == "Y")
```

## Merging dataframes

```{r data-manipulation-3.0}
temp1a <- df_jresp2 |> 
  mutate(FISH_ID.x = Male)
temp1b <- df_jresp2 |> 
  mutate(FISH_ID.y = Female)
```

```{r data-manipulation-3.1}
temp2a <- temp1a |> 
  left_join(select(df_adults_cleaned2, c("FISH_ID.x",
                                          "Sex.x",
                                          "Resting.x", 
                                          "Max.x", 
                                          "AAS.x", 
                                          "Mass.x", 
                                         "Resting_kg.x", 
                                         "Max_kg.x", 
                                         "AAS_kg.x")), 
                    by="FISH_ID.x")
```

```{r data-manipulation-3.2}
temp2b <- temp1b |> 
  left_join(select(df_adults_cleaned2, c("FISH_ID.y",
                            "Sex.y",
                            "Resting.y", 
                            "Max.y", 
                            "AAS.y", 
                            "Mass.y", 
                                         "Resting_kg.y", 
                                         "Max_kg.y", 
                                         "AAS_kg.y")), 
                   by="FISH_ID.y") 
```

```{r data-manipulation-3.3}
df_merged <- temp2a |> 
  left_join(select(temp2b, c("Clutch","Replicate", 
                             "FISH_ID.y",
                             "Resting.y", 
                             "Max.y", 
                             "AAS.y", 
                             "Mass.y", 
                             "Resting_kg.y", 
                                         "Max_kg.y", 
                                         "AAS_kg.y")), 
            by=c("Clutch","Replicate"))
```

```{r data-manipulation-3.4}
df <- df_merged |> 
  mutate(Resting_MALE =Resting_kg.x, 
         Max_MALE =Max_kg.x, 
         AAS_MALE =AAS_kg.x, 
         Mass_MALE =Mass.x, 
         FISH_ID.y =FISH_ID.x,#makes more sense for males to be .y instead of .x
         FISH_ID.x =FISH_ID.x, 
         Resting_FEMALE =Resting_kg.y, 
         Max_FEMALE =Max_kg.y, 
         AAS_FEMALE =AAS_kg.y, 
         Mass_FEMALE =Mass.y) |>  
  mutate(Max_MID =(Max_MALE+Max_FEMALE)/2) |> # easier to do it again
  mutate(Max_MID =coalesce(Max_MID, Max_MALE)) |> 
  mutate(Max_MID =coalesce(Max_MID, Max_FEMALE)) |> 
  unite("ChbSys", Chamber:System, remove=FALSE) |>
  mutate(ChbSys =factor(ChbSys)) |> 
  drop_na(Max) |> 
  filter(Max < 1.5) |>
  group_by(Clutch) |> 
  mutate(MEDIAN_Max =median(Max_kg_wet)) |> 
  ungroup() 
  #select(-c(Replicate, Chamber, System, Volume, Date_tested, Swim, Mass, Dry_mass, 18:26)) |> 
  #distinct() |> 
  #drop_na(Max_MID)
```

# Exploratory analysis 

## Offspring-Male

```{r eda-male, warning=FALSE, message=FALSE, fig.width=4, fig.height=3}
plot1 <- ggplot(df, aes(x=Max_MALE, y=Max, color=Temperature)) + 
  stat_smooth(method = "lm") +
  #geom_point(alpha=0.1) + 
  ggtitle("Offspring-male relationship") +
  xlab("Max (offspring)") + 
  ylab("Max (parental-male)") +
  theme_classic() + 
  theme(legend.position = 'right')
plot1
```

# Models

## Random factors
```{r}
modelNULL <- glmmTMB(Max ~ 1, 
                  family=gaussian(),
                  data =df)

model1 <- glmmTMB(Max ~ (1|Male), 
                  family=gaussian(),
                  data = df)

model2 <- glmmTMB(Max ~ (1|Male) + (1|ChbSys), 
                  family=gaussian(),
                  data = df) 



AIC(modelNULL, model1, model2, k=3) 
BIC(modelNULL, model1, model2)
```

## Main hypothesis

```{r}
model1a <- glmmTMB(Max_kg_wet ~ scale(as.numeric(Max_MALE), center=TRUE)*Temperature + (1| Male),    
                   family=gaussian(),
                   control = glmmTMBControl(optimizer = optim, optArgs = list(method="BFGS")),
                   data=df)
```

# Model validation {.tabset}

## DHARMa

```{r}
model1a |> 
  simulateResiduals(plot=TRUE)  

model1a |> testResiduals(plot=T)  
```

## performance 
```{r}
#performance::check_model(model1a, detrend =FALSE)
``` 

## {-}  

# Partial effect plots

```{r warning=FALSE, message=FALSE}
model1a |> ggemmeans(~Max_MALE|Temperature) |> 
  plot(add.data =TRUE) 

model1a |> ggemmeans(~Temperature) |> 
  plot(add.data =TRUE) 

model1a |> ggemmeans(~Max_MALE) |> 
  plot(add.data =TRUE)
```

# Model investigation {.tabset}

## Summary

```{r}
model1a |> summary()
```

## Anova

```{r}
model1a |> Anova()
```

## Confint

```{r}
model1a |> confint()
```

## r-squared

```{r}
model1a |> r2_nakagawa()
```

# Post-hoc 

```{r}
model1a |> emmeans(~Temperature) 
model1a |> emmeans(~Temperature) |> pairs()|> summary(adjust="tukey")
```

# Summary figure

```{r fig.height = 8, fig.width=12, warning=FALSE} 
df <- df |> drop_na(Max_kg_wet, Max_MALE)
m3.max <- emmeans(model1a, ~ Max_MALE*Temperature, 
                 at =list(Max_MALE=seq(from =min(df$Max_MALE), to =max(df$Max_MALE)+50, by=5)))

m3.max.df <- as.data.frame(m3.max)

m3.max.obs <- df |> 
  mutate(Pred =predict(model1a, re.form=NA, type ='response'), 
         Resid =residuals(model1a, type ='response'), 
         Fit =Pred+Resid) 

m3.max.obs.summarize <-  m3.max.obs |> 
  group_by(Male, Temperature) |> 
  summarise(mean.max =mean(Fit, na.rm=TRUE), 
            mean.max.male =mean(Max_MALE, na.rm = TRUE), 
            sd.max =sd(Fit, na.rm =TRUE), 
            n.max = n()) |> 
  mutate(se.max = sd.max / sqrt(n.max), 
         lower.ci.max =mean.max - qt(1-(0.05/2), n.max -1) * se.max, 
         upper.ci.max =mean.max + qt(1-(0.05/2), n.max -1) * se.max) |> 
  ungroup()

m3.max.obs.summarize2 <- m3.max.obs.summarize |> 
  group_by(Temperature) |> 
  mutate(temp_mean =mean(mean.max), 
         temp_sd =sd(mean.max)) |> 
  distinct(temp_mean, .keep_all = TRUE) 

mod = lm(mean.max ~ mean.max.male*Temperature, 
         data =m3.max.obs.summarize)
mod.max <- emmeans(mod, ~ mean.max.male*Temperature, 
                 at =list(mean.max.male=seq(from =min(m3.max.obs.summarize$mean.max.male), to =max(m3.max.obs.summarize$mean.max.male), by=5))) |> as.data.frame()

m3.plot <- ggplot(data = m3.max.df, aes(x=Max_MALE, y=emmean)) + 
  stat_smooth(data=m3.max.obs.summarize, 
              aes(x =mean.max.male,
                  y =mean.max, 
                  color=Temperature), 
              method = "lm", 
              se=FALSE) + 
  geom_ribbon(data=mod.max, 
              aes(x =mean.max.male,
                  y =emmean,
                  ymin=lower.CL,
                  ymax=upper.CL, 
                  fill=Temperature), 
              alpha=0.5) +
  geom_pointrange(data = m3.max.obs.summarize, aes(x =mean.max.male, 
                                                  y =mean.max, 
                                                  ymin =lower.ci.max, 
                                                  ymax =upper.ci.max, 
                                                  color = Temperature)) +  
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  scale_fill_manual(values =c("#69d7d8","#ff9c56", "#903146")) +
  facet_wrap(~Temperature)+
  scale_y_continuous(limits = c(500,2000), breaks = seq(500,2000,by=100))+
  xlab("PARENTAL MALE STANDARD LENGTH (mm)") + 
  ylab("OFFSPRING STANDARD LENGTH (mm)") + 
  ggtitle("Offspring-male relationship") +
  theme_classic()+theme(legend.position = 'none') 

m3.plot2 <- ggplot(m3.max.obs.summarize, aes(x=Temperature, y=mean.max, color=Temperature)) + 
  geom_pointrange(data=m3.max.obs.summarize2, 
                  aes(x=Temperature, 
                      y=temp_mean, 
                      ymin=temp_mean - temp_sd, 
                      ymax=temp_mean + temp_sd), 
                  size = 1) + 
  geom_jitter(width=0.05, 
              alpha=0.3) +  
  scale_color_manual(values = c("#69d7d8","#ff9c56", "#903146")) + 
  scale_fill_manual(values =c("#69d7d8","#ff9c56", "#903146")) +
  scale_y_continuous(limits = c(500,2000), breaks = seq(500,2000,by=100))+
  theme_classic() + 
  ylab("") + 
  theme(legend.position = c(0.8,0.9), 
                                legend.box.background = element_rect(color = "black", size=2))

m3.plot.final <-m3.plot + m3.plot2 + 
  plot_layout(guides = "collect" & theme(legend.position = "bottom"), 
              widths = c(2,1)); m3.plot.final
```

```{r eval=FALSE, echo=FALSE}
m3.density <- ggdensity(m3.max.obs, x="Fit", 
          color = "Temperature", 
          fill = "Temperature", 
          rug=TRUE, 
          add="median", 
          alpha=0.5,
          palette=c("#69d7d8","#ff9c56", "#903146")) + 
  scale_x_continuous(limits = c(500,2000), breaks = seq(500,2000,by=100))+
          clean_theme() + rotate() + 
  theme(legend.position = c(0.7,0.9), 
                                legend.box.background = element_rect(color = "black", size=2))

m3.plot.final <-m3.plot + m3.density + 
  plot_layout(guides = "collect" & theme(legend.position = "bottom"), 
              widths = c(2,1)); m3.plot.final
```

# Slopes

```{r}
add.df <- split(m3.max.obs.summarize, m3.max.obs.summarize$Temperature) |> 
  map(~lm(mean.max ~ mean.max.male, data=.)) |> 
  map(summary) |> 
  map_dbl("r.squared") |> 
  as.data.frame()

add.df <- add.df |>
  mutate(Temperature = row.names(add.df)) |>
  rename(r.sqaured =names(add.df)[1]) 

sd_values <- df |> group_by(Temperature) |> 
  summarise(sd =sd(Mass), 
            se =sd(Mass)/sqrt(nrow(df)), 
            Lower.CI =mean(Mass) - qt(1-(0.05/2), nrow(df) -1) *se, 
            Upper.CI =mean(Mass) + qt(1-(0.05/2), nrow(df) -1) *se)  

df.results.1 <- m3.max.obs.summarize |> 
  group_by(Temperature) |> 
  do({ 
    mod = lm(mean.max ~ mean.max.male, data = .) 
    data.frame(group = "Maximum", 
               slope = coef(mod)[2], 
               Heritability = coef(mod)[2]*2)
    }) |> 
  as.data.frame() |> 
  mutate(Heritability = case_when(Heritability <=0 ~ 0, 
                                  TRUE ~ Heritability)) |> 
  inner_join(add.df, by="Temperature") |> 
  inner_join(sd_values, by="Temperature"); df.results.1
``` 

# Within parental variation 

```{r}
cv_within <- m3.max.obs |> 
  group_by(Male) |> 
  mutate(mean_value =mean(Fit), 
         sd_value =sd(Fit), 
         CV =(sd_value/mean_value) * 100) |>
  ungroup() |> 
  select(-c("Replicate","Mass","Dry_mass","ChbSys","Chamber","System","Pred","Fit","Resid")) |> 
  distinct(Male, .keep_all=TRUE) 

within_var <- aov(CV ~ Temperature, 
                  data=cv_within) 
summary(within_var) 

cv_within_summ <- cv_within |> 
  group_by(Temperature) |> 
  mutate(mean_CV =mean(CV), 
         mean_mean =mean(mean_value), 
         mean_sd =mean(sd_value),
         nsample =n()) |>
  mutate(ser_value = sd_value/sqrt(nsample), 
         lower.ci =mean_CV - qt(1-(0.05/2), nsample -1) * ser_value, 
         upper.ci =mean_CV + qt(1-(0.05/2), nsample -1) * ser_value) |>
  ungroup() |> 
  distinct(Temperature, .keep_all=TRUE) |> 
  select(c("Temperature","mean_CV","mean_mean","mean_sd")) |> 
  arrange(Temperature); cv_within_summ
```

# Among parental variation
```{r}
cv_among <- cv_within |> 
  group_by(Temperature) |> 
  mutate(mean_among =mean(CV), 
         sd_among =sd(CV), 
         nsamples=n(),
         cv_among =(sd_among/mean_among)*100) |> 
  ungroup() |> 
  distinct(cv_among, .keep_all = T) |> 
  select(c("Temperature","cv_among","sd_among","mean_among","nsamples")) |> 
  arrange(Temperature)

##final cv values
cv_among2 <- data.frame(x=c("27v30","28v30","27v28"))
cv_among2$cv_among[1] =log(cv_among$cv_among[1]/cv_among$cv_among[3]) 
cv_among2$cv_among[2] =log(cv_among$cv_among[2]/cv_among$cv_among[3]) 
cv_among2$cv_among[3] =log(cv_among$cv_among[1]/cv_among$cv_among[2]) 

cv_among; cv_among2
```